---
title: "GEIER_LAB_graph_Anhedonia"
output: html_document
editor_options: 
  chunk_output_type: console
---

This document is an intro to igraph and some plotting functions.

Libraries, Data, and Working Directory

```{r}
#Working directory
setwd("C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/Cleaning_for_R/cleaning_for_R_csv/My_Regions_csv/")

#Libraries
library(psych) #For descriptive statistics
library(ggplot2) #For plotting
library(tidyverse) #For other data stuff
library(dplyr) #Data manipulation
library(stats) #For correlations
library(GGally) #For ggpairs function
library(igraph) #For various igraph stuff
library(qgraph) #For plotting graphs
library(gridExtra) #For embedding multiple figures into one figure
library(corrplot) #? Might not need

options(scipen=999) #Removes scientific notation

#Read in data
dat <- read.csv("All_subj_139roi.csv", header = TRUE)
#Look at the first few rows
head(dat)
#Get some descriptive statistics
describe(dat)
```

Correlation approach for functional connectivity. Goal is to calculate correlations among all ROIs for each group.

First step is to create a total of 2 datasets--healthy controls (HC) and depressed (MDD).

The code below uses tidyverse (specifically dplyr). I'm creating a dataset called "AGE_DAY" by taking the original data set and filtering it by AGE and DAY.

```{r}
#Healthy Control Group
hc <- dat %>% 
  filter(type == "HC")

#Group with Major Depression
mdd <- dat %>% 
  filter(type == "MDD")

```

Second step is to create correlation matrices. Cor argument uses bracket/matrix arguments. Bracketed matricies are in the form [ROW,COLUMN]. So if you only want do to math on columns 9-12 would be [ ,9:12]. If just 9 & 12 it would be [ ,c("VAR_9", "VAR_12")].  

```{r}
#Healthy Control Group
###Correlate data
hc_mat <- cor(hc[,3:141], 
                     use = "na.or.complete")
hc_mat_cingop <- cor(hc[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
hc_mat_dmode <- cor(hc[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
hc_mat_frparietal <- cor(hc[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
hc_mat_sali <- cor(hc[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
hc_mat_subc <- cor(hc[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
hc_mat_dorsalatt <- cor(hc[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network

###make matrix form
hc_mat <- as.matrix(hc_mat)
hc_mat_cingop
hc_mat_dmode 
hc_mat_frparietal
hc_mat_sali
hc_mat_subc
hc_mat_dorsalatt



#Group with Major Depression
###Correlate data
mdd_mat <- cor(mdd[,3:141], 
                     use = "na.or.complete")
mdd_mat_cingop <- cor(mdd[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
mdd_mat_dmode <- cor(mdd[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
mdd_mat_frparietal <- cor(mdd[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
mdd_mat_sali <- cor(mdd[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
mdd_mat_subc <- cor(mdd[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
mdd_mat_dorsalatt <- cor(mdd[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network


###make matrix form
mdd_mat <- as.matrix(mdd_mat)

```

Third step is to graph!

I like qgraph for the plotting features. Igraph these days seems to be more useful for calculating graph theory metrics. I'm probably not the best person to ask on this though...

Below I am compiling a total of 12 graphs. First 6 will have no threshold (i.e., all paths, sig or not, are shown on the plot)

```{r}
#All edges
#Healthy Control Group
hc_plot_all <- qgraph(hc_mat, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring") #There are many layouts. See ?qgraph

#All edges
#Group with Major Depression
mdd_plot_all <- qgraph(mdd_mat, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring") #There are many layouts. See ?qgraph

```


```{r}
#Read in csv with networks grouped together
group <- read.csv("ROIs_by_network_139_.csv", header = TRUE)
saveRDS(group, "group.rds")
group <- as.list(group)

colors <- c("red","yellow","green", "cyan", "blue", "purple")
```


Now we will also threshold to .2, not significance. We can do it by significance, but for initial passes at networks, this approach works well.

Reference: http://sachaepskamp.com/qgraph/reference/qgraph.html

```{r}
#Setting minimum to .2
#Healthy Control Group
hc_plot_2 <- qgraph(hc_mat, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "Hollywood", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = TRUE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = .9)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "Healthy Control Networks")

#Setting minimum to .2
#Group with Major Depression
mdd_plot_2 <- qgraph(mdd_mat, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", 
                             plot(1.5,0, type = "n"),
                             legend ("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = .5)
                             #sampleSize = 37) 
title(main = "Major Depression Networks")

```

Creating igraph object using "graph.adjacency" command. This is used to calculate graph theory metrics.


```{r}
g <- graph.adjacency(adult_day3_mat, mode = "undirected", weighted = TRUE)
```

Adding plots to make plot of plots

```{r}
#6 figures arranged in 1 row and 2 columns
par(mfrow = c(1,2))
plot(hc_plot_2)
plot(mdd_plot_2)
#This looks ugly. Need to change in arguments above to make look nice.
```


Some other nifty graphs that could be of use.

```{r}
dat %>% 
  filter(day == "1",
         age == "adolescent") %>%
ggpairs(columns = 5:12,
        aes(color = age),
        lower = list(continuous ="smooth", alpha = 0.3, size = 0.1))


#plot(g, layout = layout.circle)
#hub_score(g)
#degree(g)
#betweenness(g)
#all_indices(g)
```

In the future, it may be useful to create a function to do all of this with less code. Using dplyr, as I did above, can run into issues when creating functions. However, website below seems to have a general solution that should work across dplyr commands.

https://medium.com/optima-blog/writing-your-own-dplyr-functions-a1568720db0d