---
title: "GEIER_LAB_graph_Anhedonia"
output: html_document
editor_options: 
  chunk_output_type: console
---

This document uses igraph to look at some graphs & metrics for imaging resting state data.

Libraries, Data, and Working Directory

```{r}
#Working directory
setwd("C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/Cleaning_for_R/3_cleaning_for_R_csv/My_Regions_csv_n45/")

#Libraries
library(psych) #For descriptive statistics
library(ggplot2) #For plotting
library(tidyverse) #For other data stuff
library(dplyr) #Data manipulation
library(stats) #For correlations
library(GGally) #For ggpairs function
library(igraph) #For various igraph stuff
library(qgraph) #For plotting graphs
library(gridExtra) #For embedding multiple figures into one figure
library(corrplot) #? Might not need

options(scipen=999) #Removes scientific notation

#Read in data
dat <- read.csv("All_subj_139roi_.csv", header = TRUE)
dat2 <- read.csv("All_subj_139roi_3groups.csv", header = TRUE)
dat_fpdm <- read.csv("All_subj_139roi_fpdm.csv", header = TRUE)

#Look at the first few rows
head(dat)
head(dat2)
head(dat_fpdm)

#Get some descriptive statistics
describe(dat)
describe(dat2)
describe(dat_fpdm)
```

Correlation approach for functional connectivity. Goal is to calculate correlations among all ROIs for each group.

First step is to create a total of 2 datasets--healthy controls (HC) and depressed (MDD).

The code below uses tidyverse (specifically dplyr). I'm creating a dataset called "AGE_DAY" by taking the original data set and filtering it by AGE and DAY.

```{r}
#Healthy Control Group
hc <- dat %>% 
  filter(type == "HC")

#Group with Major Depression
mdd <- dat %>% 
  filter(type2 == "MDD")

##############################################################################################
#For some analyses, I will split the MDD group into Treatment Resistant Depression (TRD) & Treatment Responsive group or "Major Depression Treated" (MDT)

#HC group 
hc2 <- dat2 %>% 
  filter(types == "HC")

#TRD group
trd <- dat2 %>% 
  filter(type == "TRD")

#MDT group
mdt <- dat2 %>% 
  filter(types == "MDD")

##############################################################################################
#For some analyses, I will isolate 2 networks (e.g. FrontoParietal & Default Mode):

#Healthy Control Group
hc_fpdm <- dat_fpdm %>% 
  filter(type == "HC")

#Group with Major Depression
mdd_fpdm <- dat_fpdm %>% 
  filter(type == "MDD")

```

Second step is to create correlation matrices. Cor argument uses bracket/matrix arguments. Bracketed matricies are in the form [ROW,COLUMN]. So if you only want do to math on columns 9-12 would be [ ,9:12]. If just 9 & 12 it would be [ ,c("VAR_9", "VAR_12")].  

```{r}
#Healthy Control Group
###Correlate data
hc_mat <- cor(hc[,3:141], 
                     use = "na.or.complete") #Basically ignore the NAs
hc_mat_cingop <- cor(hc[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
hc_mat_dmode <- cor(hc[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
hc_mat_frparietal <- cor(hc[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
hc_mat_sali <- cor(hc[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
hc_mat_subc <- cor(hc[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
hc_mat_dorsalatt <- cor(hc[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
hc_mat_fpdm <- cor(hc_fpdm[,3:85], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

###make matrix form
hc_mat <- as.matrix(hc_mat)
hc_mat_cingop <- as.matrix(hc_mat_cingop)
hc_mat_dmode <- as.matrix(hc_mat_dmode)
hc_mat_frparietal <- as.matrix(hc_mat_frparietal)
hc_mat_sali <- as.matrix(hc_mat_sali)
hc_mat_subc <- as.matrix(hc_mat_subc)
hc_mat_dorsalatt <- as.matrix(hc_mat_dorsalatt)

hc_mat_fpdm <- as.matrix(hc_mat_fpdm)

#Group with Major Depression
###Correlate data
mdd_mat <- cor(mdd[,3:141], 
                     use = "na.or.complete")
mdd_mat_cingop <- cor(mdd[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
mdd_mat_dmode <- cor(mdd[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
mdd_mat_frparietal <- cor(mdd[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
mdd_mat_sali <- cor(mdd[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
mdd_mat_subc <- cor(mdd[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
mdd_mat_dorsalatt <- cor(mdd[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
mdd_mat_fpdm <- cor(mdd_fpdm[,3:85], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

###make matrix form
mdd_mat <- as.matrix(mdd_mat)
mdd_mat_cingop <- as.matrix(mdd_mat_cingop)
mdd_mat_dmode <- as.matrix(mdd_mat_dmode)
mdd_mat_frparietal <- as.matrix(mdd_mat_frparietal)
mdd_mat_sali <- as.matrix(mdd_mat_sali)
mdd_mat_subc <- as.matrix(mdd_mat_subc)
mdd_mat_dorsalatt <- as.matrix(mdd_mat_dorsalatt)

mdd_mat_fpdm <- as.matrix(mdd_mat_fpdm)


##############################################################################################
#For some analyses, I will split the MDD group into Treatment Resistant Depression (TRD) & Treatment Responsive group or "Major Depression Treated" (MDT)
#Correlate data (for Healthy Controls first)
hc_mat2 <- cor(hc2[,3:141], 
                     use = "na.or.complete") #Basically ignore the NAs
hc_mat_cingop2 <- cor(hc2[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
hc_mat_dmode2 <- cor(hc2[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
hc_mat_frparietal2 <- cor(hc2[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
hc_mat_sali2 <- cor(hc2[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
hc_mat_subc2 <- cor(hc2[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
hc_mat_dorsalatt2 <- cor(hc2[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
hc_mat_fpdm2 <- cor(hc2[,3:85], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode 

###make matrix form
hc_mat2 <- as.matrix(hc_mat2)
hc_mat_cingop2 <- as.matrix(hc_mat_cingop2)
hc_mat_dmode2 <- as.matrix(hc_mat_dmode2)
hc_mat_frparietal2 <- as.matrix(hc_mat_frparietal2)
hc_mat_sali2 <- as.matrix(hc_mat_sali2)
hc_mat_subc2 <- as.matrix(hc_mat_subc2)
hc_mat_dorsalatt2 <- as.matrix(hc_mat_dorsalatt2)

hc_mat_fpdm2 <- as.matrix(hc_mat_fpdm2)

#Group with Treatment Resistant Major Depression
###Correlate data
trd_mat <- cor(trd[,3:141], 
                     use = "na.or.complete")
trd_mat_cingop <- cor(trd[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
trd_mat_dmode <- cor(trd[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
trd_mat_frparietal <- cor(trd[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
trd_mat_sali <- cor(trd[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
trd_mat_subc <- cor(trd[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
trd_mat_dorsalatt <- cor(trd[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
trd_mat_fpdm <- cor(trd[,17:99], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

###make matrix form
trd_mat <- as.matrix(trd_mat)
trd_mat_cingop <- as.matrix(trd_mat_cingop)
trd_mat_dmode <- as.matrix(trd_mat_dmode)
trd_mat_frparietal <- as.matrix(trd_mat_frparietal)
trd_mat_sali <- as.matrix(trd_mat_sali)
trd_mat_subc <- as.matrix(trd_mat_subc)
trd_mat_dorsalatt <- as.matrix(trd_mat_dorsalatt)

trd_mat_fpdm <- as.matrix(trd_mat_fpdm)


#Group with Treatment Responsive Major Depression or MD-treated (MDT)
###Correlate data
mdt_mat <- cor(mdt[,3:141], 
                     use = "na.or.complete")
mdt_mat_cingop <- cor(mdt[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
mdt_mat_dmode <- cor(mdt[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
mdt_mat_frparietal <- cor(mdt[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
mdt_mat_sali <- cor(mdt[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
mdt_mat_subc <- cor(mdt[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
mdt_mat_dorsalatt <- cor(mdt[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
mdt_mat_fpdm <- cor(mdt[,17:99], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

###make matrix form
mdt_mat <- as.matrix(mdt_mat)
mdt_mat_cingop <- as.matrix(mdt_mat_cingop)
mdt_mat_dmode <- as.matrix(mdt_mat_dmode)
mdt_mat_frparietal <- as.matrix(mdt_mat_frparietal)
mdt_mat_sali <- as.matrix(mdt_mat_sali)
mdt_mat_subc <- as.matrix(mdt_mat_subc)
mdt_mat_dorsalatt <- as.matrix(mdt_mat_dorsalatt)

mdt_mat_fpdm <- as.matrix(mdt_mat_fpdm)
```

Third step is to graph!

I like qgraph for the plotting features. Igraph these days seems to be more useful for calculating graph theory metrics. I'm probably not the best person to ask on this though...

Below I am compiling a total of 12 graphs. First 6 will have no threshold (i.e., all paths, sig or not, are shown on the plot)

```{r}
#All edges
#Healthy Control Group
hc_plot_all <- qgraph(hc_mat, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring") #There are many layouts. See ?qgraph

#All edges
#Group with Major Depression
mdd_plot_all <- qgraph(mdd_mat, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring") #There are many layouts. See ?qgraph

```


```{r}
#Read in csv with networks grouped together
group <- read.csv("ROIs_by_network_139_.csv", header = TRUE)
saveRDS(group, "group.rds")
group <- as.list(group)

group_dm <- read.csv("ROIs_by_network_dm.csv", header = TRUE)
saveRDS(group_dm, "group_dm.rds")
group_dm <- as.list(group_dm)

group_fpdm2 <- read.csv("ROIs_by_network_fpdm2.csv", header = TRUE)
saveRDS(group_fpdm2, "group_fpdm2.rds")
group_fpdm2 <- as.list(group_fpdm2)


colors <- c("red","yellow","green", "cyan", "blue", "purple")

colors_co <- c("red")
colors_dm <- c("yellow")
colors_fp <- c("green")
colors_sal <- c("cyan")
colors_sub <- c("blue")
colors_da <- c("purple")
colors_fpdm <- c("yellow","green")
```


Now we will also threshold to .2, not significance. We can do it by significance, but for initial passes at networks, this approach works well.

Reference: http://sachaepskamp.com/qgraph/reference/qgraph.html

```{r}
#Setting minimum to .2
#Healthy Control Group
hc_plot_2 <- qgraph(hc_mat, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = TRUE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "Healthy Control Networks")

#Setting minimum to .2
#Group with Major Depression
mdd_plot_2 <- qgraph(mdd_mat, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "Major Depression Networks")

```


```{r}
#graphing by network (Healthy Controls):
#Setting minimum to .2

#Healthy Control Group - CinguloOpercular Network 
hc_plot_cingop <- qgraph(hc_mat_cingop, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_co, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC CinguloOpercular Network")


#Major Depression Group - CinguloOpercular Network 
mdd_plot_cingop <- qgraph(mdd_mat_cingop, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_co, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD CinguloOpercular Network")


#####################################################################################
#Healthy Control Group - Default Mode Network 
hc_plot_dmode <- qgraph(hc_mat_dmode, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Default Mode Network")


#Major Depression Group - Default Mode Network 
mdd_plot_dmode <- qgraph(mdd_mat_dmode, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Default Mode Network")


#####################################################################################
#Healthy Control Group - Frontal Parietal Network 
hc_plot_frparietal <- qgraph(hc_mat_frparietal, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_fp, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Frontal Parietal Network")


#Major Depression Group - Frontal Parietal Network 
mdd_plot_frparietal <- qgraph(mdd_mat_frparietal, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fp, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Frontal Parietal Network")


#####################################################################################
#Healthy Control Group - Salience Network 
hc_plot_sali <- qgraph(hc_mat_sali, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Salience Network")


#Major Depression Group - Salience Network 
mdd_plot_sali <- qgraph(mdd_mat_sali, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Salience Network")


#####################################################################################
#Healthy Control Group - Subcortical Network 
hc_plot_subc <- qgraph(hc_mat_subc, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Subcortical Network")


#Major Depression Group - Subcortical Network 
mdd_plot_subc <- qgraph(mdd_mat_subc, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Subcortical Network")


#####################################################################################
#Healthy Control Group - Dorsal Attention Network 
hc_plot_dorsalatt <- qgraph(hc_mat_dorsalatt, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_da, #applies a customized list of colors
                             vsize = 6, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Dorsal Attention Network")


#Major Depression Group - Dorsal Attention Network 
mdd_plot_dorsalatt <- qgraph(mdd_mat_dorsalatt, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_da, #applies a customized list of colors
                             vsize = 6, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Dorsal Attention Network")
```


```{r}
#graphing ***between*** network (Healthy Controls):
#Setting minimum to .2

#Healthy Control Group - FrontoParietal & Default Mode Networks
hc_plot_fpdm <- qgraph(hc_mat_fpdm2, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC FrontoParietal & Default Mode Networks")


#Major Depression Treated (not TRD) Group - FrontoParietal & Default Mode Networks
mdt_plot_fpdm <- qgraph(mdt_mat_fpdm, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT FrontoParietal & Default Mode Networks")


#Major Depression Treated (not TRD) Group - FrontoParietal & Default Mode Networks
trd_plot_fpdm <- qgraph(trd_mat_fpdm, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD FrontoParietal & Default Mode Networks")
```


```{r}
##############################################################################################
#For some analyses, I will split the MDD group into Treatment Resistant Depression (TRD) & Treatment Responsive group or "Major Depression Treated" (MDT)
#Graph data (for Healthy Controls first)

#Setting minimum to .2
#Healthy Control Group
hc2_plot_2 <- qgraph(hc_mat2, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = TRUE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "Healthy Control Networks")

#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_2 <- qgraph(trd_mat, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = TRUE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Networks")


#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_2 <- qgraph(mdt_mat, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD - Treated Networks")
```


Creating igraph object using "graph.adjacency" command. This is used to calculate graph theory metrics.

```{r}
g <- graph.adjacency(adult_day3_mat, mode = "undirected", weighted = TRUE)
```

Adding plots to make plot of plots

```{r}
#6 figures arranged in 1 row and 2 columns
par(mfrow = c(1,2))
plot(hc_plot_2)
plot(mdd_plot_2)
#This looks ugly. Need to change in arguments above to make look nice.

#OR
par(mfrow = c(1,2))
plot(hc_plot_cingop)
plot(mdd_plot_cingop)

#OR
par(mfrow = c(1,2))
plot(hc_plot_dmode)
plot(mdd_plot_dmode)

#OR
par(mfrow = c(1,2))
plot(hc_plot_dorsalatt)
plot(mdd_plot_dorsalatt)

#OR
par(mfrow = c(1,3))
plot(hc2_plot_2)
plot(trd_plot_2)
plot(mdt_plot_2)

#OR
par(mfrow = c(1,2))
plot(trd_plot_2)
plot(mdt_plot_2)

#OR
par(mfrow = c(1,3))
plot(hc_plot_fpdm)
plot(trd_plot_fpdm)
plot(mdt_plot_fpdm)
```


```{r}
#Taking the average of the entire matrices:
colMeans_hc_all <- colMeans(hc_mat2)
mean(colMeans_hc_fpdm)

colMeans_mdt_all <- colMeans(mdt_mat)
mean(colMeans_mdt_fpdm)

colMeans_trd_all <- colMeans(trd_mat)
mean(colMeans_trd_fpdm)


#for the fpdm networks
colMeans_hc_fpdm <- colMeans(hc_mat_fpdm2)
mean(colMeans_hc_fpdm)

colMeans_mdt_fpdm <- colMeans(mdt_mat_fpdm)
mean(colMeans_mdt_fpdm)

colMeans_trd_fpdm <- colMeans(trd_mat_fpdm)
mean(colMeans_trd_fpdm)
```


Some other nifty graphs that could be of use.

```{r}
dat %>% 
  filter(day == "1",
         age == "adolescent") %>%
ggpairs(columns = 5:12,
        aes(color = age),
        lower = list(continuous ="smooth", alpha = 0.3, size = 0.1))


#Modularity score - higher score means more modular

#hub score - highest hub sore --> identifying nodes


#plot(g, layout = layout.circle)
#hub_score(g) 
#degree(g)
#betweenness(g)
#all_indices(g)
```

In the future, it may be useful to create a function to do all of this with less code. Using dplyr, as I did above, can run into issues when creating functions. However, website below seems to have a general solution that should work across dplyr commands.

https://medium.com/optima-blog/writing-your-own-dplyr-functions-a1568720db0d