---
title: "GEIER_LAB_graph_Anhedonia_Individual_Maps"
output: html_document
editor_options: 
  chunk_output_type: console
---

This document uses igraph to look at some graphs & metrics for imaging resting state data.

Libraries, Data, and Working Directory

```{r}
#Working directory
setwd("C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/Cleaning_for_R/3_cleaning_for_R_csv/My_Regions_csv_n45")

#Libraries
library(psych) #For descriptive statistics
library(ggplot2) #For plotting
library(tidyverse) #For other data stuff
library(dplyr) #Data manipulation
library(stats) #For correlations
library(GGally) #For ggpairs function
library(igraph) #For various igraph stuff
library(qgraph) #For plotting graphs
library(gridExtra) #For embedding multiple figures into one figure
library(corrplot) #? Might not need

options(scipen=999) #Removes scientific notation

#Read in data
dat <- read.csv("No859_subj_139roi_2groups.csv", header = TRUE)
dat3 <- read.csv("No859_subj_139roi_3groups.csv", header = TRUE)
dat_fpdm <- read.csv("No859_All_subj_139roi_fpdm.csv", header = TRUE)  #2 groups (MDD & HC)
dat_cingdm <- read.csv("No859_subj_139roi_cingdm.csv", header = TRUE)
dat_saldm <- read.csv("No859_subj_139roi_saldm.csv", header = TRUE)

#Look at the first few rows
head(dat)
head(dat3)
head(dat_fpdm)

#Get some descriptive statistics
describe(dat)
describe(dat3)
describe(dat_fpdm)
```

Correlation approach for functional connectivity. Goal is to calculate correlations among all ROIs for each group.

First step is to create a total of 2 datasets--healthy controls (HC) and depressed (MDD).

The code below uses tidyverse (specifically dplyr). I'm creating datasets called hc & mdd by taking the original data set and filtering it by group (column title = "types").

```{r}
#Healthy Control Group
hc <- dat %>% 
  filter(type == "HC")

#Group with Major Depression
mdd <- dat %>% 
  filter(type == "MDD")

##############################################################################################
#For some analyses, I will split the MDD group into Treatment Resistant Depression (TRD) & Treatment Responsive group or "Major Depression Treated" (MDT)

#HC group 
hc2 <- dat3%>% 
  filter(types == "HC")

#TRD group
trd <- dat3%>% 
  filter(types == "TRD")

#MDT group
mdt <- dat3 %>% 
  filter(types == "MDD")

##############################################################################################
#For some analyses, I will isolate 2 networks (e.g. FrontoParietal & Default Mode):

#Healthy Control Group
hc_fpdm <- dat_fpdm %>% 
  filter(type == "HC")

#Group with Major Depression
mdd_fpdm <- dat_fpdm %>% 
  filter(type == "MDD")


#For some analyses, I will isolate 2 networks (e.g. Cingulo-Opercular & Default Mode):

#Healthy Control Group
hc_cingdm <- dat_cingdm %>% 
  filter(type == "HC")

#Group with Major Depression
mdd_cingdm <- dat_cingdm %>% 
  filter(type == "MDD")


#For some analyses, I will isolate 2 networks (e.g. Salience & Default Mode):

#Healthy Control Group
hc_saldm <- dat_saldm %>% 
  filter(type == "HC")

#Group with Major Depression
mdd_saldm <- dat_saldm %>% 
  filter(type == "MDD")
```

Second step is to create correlation matrices. Cor argument uses bracket/matrix arguments. Bracketed matricies are in the form [ROW,COLUMN]. So if you only want do to math on columns 9-12 would be [ ,9:12]. If just 9 & 12 it would be [ ,c("VAR_9", "VAR_12")].  

```{r}
#Healthy Control Group
###Correlate data
hc_mat <- cor(hc[,3:141], 
                     use = "na.or.complete") #Basically ignore the NAs
hc_mat_cingop <- cor(hc[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
hc_mat_dmode <- cor(hc[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
hc_mat_frparietal <- cor(hc[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
hc_mat_sali <- cor(hc[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
hc_mat_subc <- cor(hc[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
hc_mat_dorsalatt <- cor(hc[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
hc_mat_fpdm <- cor(hc_fpdm[,3:85], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal networks

hc_mat_cingdm <- cor(hc_cingdm[,3:74],  
                     use = "na.or.complete") #gives matrix for default mode & cingulo-opercular networks

hc_mat_saldm <- cor(hc_saldm[,3:78],  
                     use = "na.or.complete") #gives matrix for default mode & cingulo-opercular networks


###make matrix form
hc_mat <- as.matrix(hc_mat)
hc_mat_cingop <- as.matrix(hc_mat_cingop)
hc_mat_dmode <- as.matrix(hc_mat_dmode)
hc_mat_frparietal <- as.matrix(hc_mat_frparietal)
hc_mat_sali <- as.matrix(hc_mat_sali)
hc_mat_subc <- as.matrix(hc_mat_subc)
hc_mat_dorsalatt <- as.matrix(hc_mat_dorsalatt)

hc_mat_fpdm <- as.matrix(hc_mat_fpdm)
hc_mat_cingdm <- as.matrix(hc_mat_cingdm)
hc_mat_saldm <- as.matrix(hc_mat_saldm)

#Group with Major Depression
###Correlate data
mdd_mat <- cor(mdd[,3:141], 
                     use = "na.or.complete")
mdd_mat_cingop <- cor(mdd[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
mdd_mat_dmode <- cor(mdd[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
mdd_mat_frparietal <- cor(mdd[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
mdd_mat_sali <- cor(mdd[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
mdd_mat_subc <- cor(mdd[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
mdd_mat_dorsalatt <- cor(mdd[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
mdd_mat_fpdm <- cor(mdd_fpdm[,3:85], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

mdd_mat_cingdm <- cor(mdd_cingdm[,3:74], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

mdd_mat_saldm <- cor(mdd_saldm[,3:78], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks


###make matrix form
mdd_mat <- as.matrix(mdd_mat)
mdd_mat_cingop <- as.matrix(mdd_mat_cingop)
mdd_mat_dmode <- as.matrix(mdd_mat_dmode)
mdd_mat_frparietal <- as.matrix(mdd_mat_frparietal)
mdd_mat_sali <- as.matrix(mdd_mat_sali)
mdd_mat_subc <- as.matrix(mdd_mat_subc)
mdd_mat_dorsalatt <- as.matrix(mdd_mat_dorsalatt)

mdd_mat_fpdm <- as.matrix(mdd_mat_fpdm)
mdd_mat_cingdm <- as.matrix(mdd_mat_cingdm)
mdd_mat_saldm <- as.matrix(mdd_mat_saldm)

##############################################################################################
#For some analyses, I will split the MDD group into Treatment Resistant Depression (TRD) & Treatment Responsive group or "Major Depression Treated" (MDT)
#Correlate data (for Healthy Controls first)
hc_mat2 <- cor(hc2[,3:141], 
                     use = "na.or.complete") #Basically ignore the NAs
hc_mat_cingop2 <- cor(hc2[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
hc_mat_dmode2 <- cor(hc2[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
hc_mat_frparietal2 <- cor(hc2[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
hc_mat_sali2 <- cor(hc2[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
hc_mat_subc2 <- cor(hc2[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
hc_mat_dorsalatt2 <- cor(hc2[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
hc_mat_fpdm2 <- cor(hc2[,3:85], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode 

###make matrix form
hc_mat2 <- as.matrix(hc_mat2)
hc_mat_cingop2 <- as.matrix(hc_mat_cingop2)
hc_mat_dmode2 <- as.matrix(hc_mat_dmode2)
hc_mat_frparietal2 <- as.matrix(hc_mat_frparietal2)
hc_mat_sali2 <- as.matrix(hc_mat_sali2)
hc_mat_subc2 <- as.matrix(hc_mat_subc2)
hc_mat_dorsalatt2 <- as.matrix(hc_mat_dorsalatt2)

hc_mat_fpdm2 <- as.matrix(hc_mat_fpdm2)

#Group with Treatment Resistant Major Depression
###Correlate data
trd_mat <- cor(trd[,3:141], 
                     use = "na.or.complete")
trd_mat_cingop <- cor(trd[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
trd_mat_dmode <- cor(trd[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
trd_mat_frparietal <- cor(trd[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
trd_mat_sali <- cor(trd[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
trd_mat_subc <- cor(trd[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
trd_mat_dorsalatt <- cor(trd[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
trd_mat_fpdm <- cor(trd[,17:99], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

###make matrix form
trd_mat <- as.matrix(trd_mat)
trd_mat_cingop <- as.matrix(trd_mat_cingop)
trd_mat_dmode <- as.matrix(trd_mat_dmode)
trd_mat_frparietal <- as.matrix(trd_mat_frparietal)
trd_mat_sali <- as.matrix(trd_mat_sali)
trd_mat_subc <- as.matrix(trd_mat_subc)
trd_mat_dorsalatt <- as.matrix(trd_mat_dorsalatt)

trd_mat_fpdm <- as.matrix(trd_mat_fpdm)


#Group with Treatment Responsive Major Depression or MD-treated (MDT)
###Correlate data
mdt_mat <- cor(mdt[,3:141], 
                     use = "na.or.complete")
mdt_mat_cingop <- cor(mdt[,3:16], 
                     use = "na.or.complete") #gives matrix for cinguloOpercular network
mdt_mat_dmode <- cor(mdt[,17:74], 
                     use = "na.or.complete") #gives matrix for default mode network
mdt_mat_frparietal <- cor(mdt[,75:99], 
                     use = "na.or.complete") #gives matrix for frontoParietal network
mdt_mat_sali <- cor(mdt[,100:117], 
                     use = "na.or.complete") #gives matrix for salience network
mdt_mat_subc <- cor(mdt[,118:130], 
                     use = "na.or.complete") #gives matrix for subcortical network
mdt_mat_dorsalatt <- cor(mdt[,131:141], 
                     use = "na.or.complete") #gives matrix for dorsal attention network
mdt_mat_fpdm <- cor(mdt[,17:99], 
                     use = "na.or.complete") #gives matrix for default mode & frontoparietal mode networks

###make matrix form
mdt_mat <- as.matrix(mdt_mat)
mdt_mat_cingop <- as.matrix(mdt_mat_cingop)
mdt_mat_dmode <- as.matrix(mdt_mat_dmode)
mdt_mat_frparietal <- as.matrix(mdt_mat_frparietal)
mdt_mat_sali <- as.matrix(mdt_mat_sali)
mdt_mat_subc <- as.matrix(mdt_mat_subc)
mdt_mat_dorsalatt <- as.matrix(mdt_mat_dorsalatt)

mdt_mat_fpdm <- as.matrix(mdt_mat_fpdm)
```

Third step is to graph!

I like qgraph for the plotting features. Igraph these days seems to be more useful for calculating graph theory metrics. I'm probably not the best person to ask on this though...

Below I am compiling 2 graphs with no threshold (i.e., all paths, sig or not, are shown on the plot)

```{r}
#All edges
#Healthy Control Group
hc_plot_all <- qgraph(hc_mat, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring") #There are many layouts. See ?qgraph

#All edges
#Group with Major Depression
mdd_plot_all <- qgraph(mdd_mat, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring") #There are many layouts. See ?qgraph

```


```{r}
#Read in csv with networks grouped together
group <- read.csv("ROIs_by_network_139_.csv", header = TRUE)
saveRDS(group, "group.rds")
group <- as.list(group)

group_dm <- read.csv("ROIs_by_network_dm.csv", header = TRUE)
saveRDS(group_dm, "group_dm.rds")
group_dm <- as.list(group_dm)

group_fpdm2 <- read.csv("ROIs_by_network_fpdm2.csv", header = TRUE)
saveRDS(group_fpdm2, "group_fpdm2.rds")
group_fpdm2 <- as.list(group_fpdm2)

group_cingdm <- read.csv("ROIs_by_network_cingdm.csv", header = TRUE)
saveRDS(group_cingdm, "group_cingdm.rds")
group_cingdm <- as.list(group_cingdm)

group_saldm <-
read.csv("ROIs_by_network_saldm.csv", header = TRUE)
saveRDS(group_saldm, "group_saldm.rds")
group_saldm <- as.list(group_saldm)


colors <- c("red","yellow","green", "cyan", "blue", "purple")

colors_co <- c("red")
colors_dm <- c("yellow")
colors_fp <- c("green")
colors_sal <- c("cyan")
colors_sub <- c("blue")
colors_da <- c("purple")
colors_fpdm <- c("yellow","green")
colors_cingdm <- c("red","yellow")
colors_saldm <- c("yellow","cyan")
```


Now we will also threshold to .2, not significance. We can do it by significance, but for initial passes at networks, this approach works well.

Reference: http://sachaepskamp.com/qgraph/reference/qgraph.html

```{r}
#Setting minimum to .2
#Healthy Control Group
hc_plot_2 <- qgraph(hc_mat_p, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = 0.2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "Healthy Control Networks", line =3)

#Setting minimum to .2
#Group with Major Depression
mdd_plot_2 <- qgraph(mdd_mat_p, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = 0.2)
                             #sampleSize = 45) 
title(main = "Major Depression Networks", line =3)

```


```{r}
#graphing by network (Healthy Controls):
#Setting minimum to .2

#Healthy Control Group - Cingulo-Opercular Network 
hc_plot_cingop <- qgraph(hc_mat_cingop_p, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_co, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Cingulo-Opercular Network", line=3)


#Major Depression Group - CinguloOpercular Network 
mdd_plot_cingop <- qgraph(mdd_mat_cingop_p, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_co, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Cingulo-Opercular Network", line=3)


#####################################################################################
#Healthy Control Group - Default Mode Network 
hc_plot_dmode <- qgraph(hc_mat_dmode_p , 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Default Mode Network", line = 3)


#Major Depression Group - Default Mode Network 
mdd_plot_dmode <- qgraph(mdd_mat_dmode_p, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Default Mode Network", line = 3)


#####################################################################################
#Healthy Control Group - Fronto-Parietal Network 
hc_plot_frparietal <- qgraph(hc_mat_frparietal, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_fp, #applies a customized list of colors
                             vsize = 4 #This changes the size of the vertices (nodes)
                             #minimum = .2
                            )   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Fronto-Parietal Network", line = 3)


#Major Depression Group - Frontal Parietal Network 
mdd_plot_frparietal <- qgraph(mdd_mat_frparietal, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fp, #applies a customized list of colors
                             vsize = 4 #This changes the size of the vertices (nodes)
                            # minimum = .2
                            )
                             #sampleSize = 45) 
title(main = "MDD Fronto-Parietal Network", line = 3)


#####################################################################################
#Healthy Control Group - Salience Network 
hc_plot_sali <- qgraph(hc_mat_sali_p, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Salience Network", line = 3)


#Major Depression Group - Salience Network 
mdd_plot_sali <- qgraph(mdd_mat_sali_p, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Salience Network", line = 3)


#####################################################################################
#Healthy Control Group - Subcortical Network 
hc_plot_subc <- qgraph(hc_mat_subc_p, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Subcortical Network", line = 3)


#Major Depression Group - Subcortical Network 
mdd_plot_subc <- qgraph(mdd_mat_subc_p, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Subcortical Network", line = 3)


#####################################################################################
#Healthy Control Group - Dorsal Attention Network 
hc_plot_dorsalatt <- qgraph(hc_mat_dorsalatt_p, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_da, #applies a customized list of colors
                             vsize = 6, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Dorsal Attention Network", line = 3)


#Major Depression Group - Dorsal Attention Network 
mdd_plot_dorsalatt <- qgraph(mdd_mat_dorsalatt_p, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group_dm,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_da, #applies a customized list of colors
                             vsize = 6, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDD Dorsal Attention Network", line = 3)
```


```{r}
#graphing ***between*** network (Healthy Controls):
#Setting minimum to .2

#Healthy Control Group - FrontoParietal & Default Mode Networks
hc_plot_fpdm <- qgraph(hc_mat_fpdm2, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Fronto-Parietal & Default Mode Networks", line=3)


mdd_plot_fpdm <- qgraph(mdd_mat_fpdm, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "MDD  Fronto-Parietal & Default Mode Networks", line=3)

###################################################


#graphing ***between*** network (Healthy Controls):
#Setting minimum to .2

#Healthy Control Group -	Cingulo-opercular & Default Mode Networks
hc_plot_cingdm <- qgraph(hc_mat_cingdm, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_cingdm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_cingdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC 	Cingulo-opercular & Default Mode Networks", line=3)


mdd_plot_cingdm <- qgraph(mdd_mat_cingdm, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_cingdm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_cingdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "MDD 	Cingulo-opercular & Default Mode Networks", line=3)


#########################################

#graphing ***between*** network (Healthy Controls):
#Setting minimum to .2

#Healthy Control Group -	Salience & Default Mode Networks
hc_plot_saldm <- qgraph(hc_mat_saldm, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_saldm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                            colors = colors_saldm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC 	Salience & Default Mode Networks", line=3)


mdd_plot_saldm <- qgraph(mdd_mat_saldm, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_saldm, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                          colors = colors_saldm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "MDD 	Salience & Default Mode Networks", line=3)


###################################################

#Major Depression Treated (not TRD) Group - FrontoParietal & Default Mode Networks
mdt_plot_fpdm <- qgraph(mdt_mat_fpdm, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Fronto-Parietal & Default Mode Networks", line=3)


#Major Depression TRD Group - FrontoParietal & Default Mode Networks
trd_plot_fpdm <- qgraph(trd_mat_fpdm, #oR mdd_mat_cingop, mdd_mat_dmode, mdd_mat_frparietal, mdd_mat_sali, mdd_mat_subc, mdd_mat_dorsalatt
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group_fpdm2,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE,
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fpdm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Fronto-Parietal & Default Mode Networks", line=3)
```


```{r}
##############################################################################################
#For some analyses, I will split the MDD group into Treatment Resistant Depression (TRD) & Treatment Responsive group or "Major Depression Treated" (MDT)
#Graph data (for Healthy Controls first)

#Setting minimum to .2
#Healthy Control Group
hc2_plot_2 <- qgraph(hc_mat2_p, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = TRUE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = 0.2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "Healthy Control Networks")



#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_2 <- qgraph(mdt_mat_p, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = 0.2)
                             #sampleSize = 45) 
title(main = "MDD - Treated Networks")


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_2 <- qgraph(trd_mat_p, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = 0.2)
                             #sampleSize = 45) 
title(main = "TRD Networks")
```

```{r}
######################################################################
#More Individual Network maps (but with 3 groups)
#Setting minimum to .2
#Healthy Control Group - CinguloOpercular Network
hc2_plot_cingop <- qgraph(hc_mat_cingop2, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Cingulo-Opercular Network", line = 3)

#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_cingop <- qgraph(mdt_mat_cingop, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Cingulo-Opercular Network", line=3)


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_cingop <- qgraph(trd_mat_cingop, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Cingulo-Opercular Network", line=3)

```

```{r}
######################################################################
#More Individual Network maps (but with 3 groups)
#Setting minimum to .2
#Healthy Control Group - Default Mode Network
hc2_plot_dmode <- qgraph(hc_mat_dmode2, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Default Mode Network", line = 3)

#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_dmode <- qgraph(mdt_mat_dmode, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Default Mode Network", line=3)


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_dmode <- qgraph(trd_mat_dmode, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_dm, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Default Mode Network", line=3)
```

```{r}
######################################################################
#More Individual Network maps (but with 3 groups)
#Setting minimum to .2
#Healthy Control Group - Fronto-parietal Network
hc2_plot_frparietal <- qgraph(hc_mat_frparietal2, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fp, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Fronto-Parietal Network", line = 3)

#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_frparietal <- qgraph(mdt_mat_frparietal, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fp, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Fronto-Parietal Network", line=3)


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_frparietal <- qgraph(trd_mat_frparietal, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_fp, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Fronto-Parietal Network", line=3)
```


```{r}
######################################################################
#More Individual Network maps (but with 3 groups)
#Setting minimum to .2
#Healthy Control Group - Salience Network
hc2_plot_sali <- qgraph(hc_mat_sali2, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Salience Network", line = 3)

#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_sali <- qgraph(mdt_mat_sali, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Salience Network", line=3)


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_sali <- qgraph(trd_mat_sali, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sal, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Salience Network", line=3)
```


```{r}
######################################################################
#More Individual Network maps (but with 3 groups)
#Setting minimum to .2
#Healthy Control Group - Subcortical Network
hc2_plot_subc <- qgraph(hc_mat_subc2, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Subcortical Network", line = 3)

#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_subc <- qgraph(mdt_mat_subc, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Subcortical Network", line=3)


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_subc <- qgraph(trd_mat_subc, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_sub, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Subcortical Network", line=3)
```


```{r}
######################################################################
#More Individual Network maps (but with 3 groups)
#Setting minimum to .2
#Healthy Control Group - Dorsal Attention Network
hc2_plot_dorsalatt <- qgraph(hc_mat_dorsalatt2, 
                             edge.labels = TRUE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_da, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "HC Dorsal Attention Network", line = 3)

#Setting minimum to .2
#Group with Major Depression Treated (MDT), i.e. not TRD
mdt_plot_dorsalatt <- qgraph(mdt_mat_dorsalatt, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_da, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "MDT Dorsal Attention Network", line=3)


#Setting minimum to .2
#Group with Treatment Resistant Major Depression
trd_plot_dorsalatt <- qgraph(trd_mat_dorsalatt, 
                             edge.labels = TRUE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             #groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             #overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors_da, #applies a customized list of colors
                             vsize = 4, #This changes the size of the vertices (nodes)
                             minimum = .2)
                             #sampleSize = 45) 
title(main = "TRD Dorsal Attention Network", line=3)
```



Adding plots to make plot of plots (i.e. arranging plots in a row/grid)
```{r}
#6 figures arranged in 1 row and 2 columns
par(mfrow = c(1,2))
plot(hc_plot_2)
plot(mdd_plot_2)


#OR
par(mfrow = c(1,2))
plot(hc_plot_cingop)
plot(mdd_plot_cingop)

#OR
par(mfrow = c(1,2))
plot(hc_plot_dmode)
plot(mdd_plot_dmode)

#OR
par(mfrow = c(1,2))
plot(hc_plot_dorsalatt)
plot(mdd_plot_dorsalatt)

#OR
par(mfrow = c(1,3))
plot(hc2_plot_2)
plot(trd_plot_2)
plot(mdt_plot_2)

#OR
par(mfrow = c(1,2))
plot(hc_plot_fpdm)
plot(mdd_plot_fpdm)

#OR
par(mfrow = c(1,3))
plot(hc_plot_fpdm)
plot(mdt_plot_fpdm)
plot(trd_plot_fpdm)

#OR #3 groups (HC, MDT, TRD) with and w/o Subject 859
par(mfrow = c(1,3))
plot(hc2_plot_2)
plot(mdt_plot_2)
plot(trd_plot_2)
plot(hc2_plot_no859)
plot(mdt_plot_2)
plot(trd_plot_2)


#Strength distribution graph
par(mfrow = c(1,1))
plot(sd_hc)
```


```{r}
#Taking the average of the entire matrices:
colMeans_hc <- colMeans(hc_mat)
mean(colMeans_hc)
mean(hc_mat) #This should give the same answer as the previous two lines of code combined'
std_hc <- SD(hc_mat)
stdev_hc <- mean(std_hc)

colMeans_mdd <- colMeans(mdd_mat)
mean(colMeans_mdd)
mean(mdd_mat) #This should give the same answer as the previous two lines of code combined
std_mdd <- SD(mdd_mat)
stdev_mdd <- mean(std_mdd)


#Taking the averages & std. deviations of the entire matrices:
mean(hc_mat2)
std_hc2 <- SD(hc_mat2)
stdev_hc <- mean(std_hc2)

mean(mdt_mat)
std_mdt <- SD(mdt_mat)
stdev_mdt <- mean(std_mdt)

mean(trd_mat)
std_trd <- SD(trd_mat)
stdev_trd <- mean(std_trd)

######## t-test ########

t.test(hc_mat,mdd_mat,alternative="two.sided",na.action=na.remove)

######## t-test ########




#for the fpdm networks
mean(hc_mat_fpdm2)

mean(mdt_mat_fpdm)

mean(trd_mat_fpdm)

#With Subject 859 removed:
mean(hc_no859_mat)
std_hc_no859 <- SD(hc_no859_mat)
stdev_hc_no859 <- mean(std_hc_no859)

mean(mdt_mat)
std_mdt <- SD(mdt_mat)
stdev_mdt <- mean(std_mdt)

mean(trd_mat)
std_trd <- SD(trd_mat)
stdev_trd <- mean(std_trd)


######## ANOVA ########

#I might need to put all the matrices into one and have a separate column for "group" to do this...

```


Some other nifty graphs that could be of use.
```{r} 
#I'm not sure what this chunk does

dat %>% 
  filter(day == "1",
         age == "adolescent") %>%
ggpairs(columns = 5:12,
        aes(color = age),
        lower = list(continuous ="smooth", alpha = 0.3, size = 0.1))


```



Turn negative values to 0's in all matrices:
```{r}
hc_mat_p <- pmax(hc_mat,0)
hc_mat_cingdm_p <- pmax(hc_mat_cingdm,0)
hc_mat_cingop_p <- pmax(hc_mat_cingop,0)
hc_mat_dmode_p <- pmax(hc_mat_dmode,0)
hc_mat_dorsalatt_p <- pmax(hc_mat_dorsalatt,0)
hc_mat_fpdm_p <- pmax(hc_mat_fpdm,0)
hc_mat_frparietal_p <- pmax(hc_mat_frparietal,0)
hc_mat_saldm_p <- pmax(hc_mat_saldm,0)
hc_mat_sali_p <- pmax(hc_mat_sali,0)
hc_mat_subc_p <- pmax(hc_mat_subc,0)

hc_mat2_p <- pmax(hc_mat2,0)
hc_mat_cingop2_p <- pmax(hc_mat_cingop2,0)
hc_mat_dmode2_p <- pmax(hc_mat_dmode2,0)
hc_mat_dorsalatt2_p <- pmax(hc_mat_dorsalatt2,0)
hc_mat_fpdm2_p <- pmax(hc_mat_fpdm2,0)
hc_mat_frparietal2_p <- pmax(hc_mat_frparietal2,0)
hc_mat_sali2_p <- pmax(hc_mat_sali2,0)
hc_mat_subc2_p <- pmax(hc_mat_subc2,0)

mdd_mat_p <- pmax(mdd_mat,0)
mdd_mat_cingdm_p <- pmax(mdd_mat_cingdm,0)
mdd_mat_cingop_p <- pmax(mdd_mat_cingop,0)
mdd_mat_dmode_p <- pmax(mdd_mat_dmode,0)
mdd_mat_dorsalatt_p <- pmax(mdd_mat_dorsalatt,0)
mdd_mat_fpdm_p <- pmax(mdd_mat_fpdm,0)
mdd_mat_frparietal_p <- pmax(mdd_mat_frparietal,0)
mdd_mat_saldm_p <- pmax(mdd_mat_saldm,0)
mdd_mat_sali_p <- pmax(mdd_mat_sali,0)
mdd_mat_subc_p <- pmax(mdd_mat_subc,0)

mdt_mat_p <- pmax(mdt_mat,0)
mdt_mat_cingop_p <- pmax(mdt_mat_cingop,0)
mdt_mat_dmode_p <- pmax(mdt_mat_dmode,0)
mdt_mat_dorsalatt_p <- pmax(mdt_mat_dorsalatt,0)
mdt_mat_fpdm_p <- pmax(mdt_mat_fpdm,0)
mdt_mat_frparietal_p <- pmax(mdt_mat_frparietal,0)
mdt_mat_sali_p <- pmax(mdt_mat_sali,0)
mdt_mat_subc_p <- pmax(mdt_mat_subc,0)

trd_mat_p <- pmax(trd_mat,0)
trd_mat_cingop_p <- pmax(trd_mat_cingop,0)
trd_mat_dmode_p <- pmax(trd_mat_dmode,0)
trd_mat_dorsalatt_p <- pmax(trd_mat_dorsalatt,0)
trd_mat_fpdm_p <- pmax(trd_mat_fpdm,0)
trd_mat_frparietal_p <- pmax(trd_mat_frparietal,0)
trd_mat_sali_p <- pmax(trd_mat_sali,0)
trd_mat_subc_p <- pmax(trd_mat_subc,0)
```

```{r}
#Graphing 3 groups (HC, MDT, TRD) at dif thresholds:

hc_plot_p <- qgraph(hc_mat_p, 
                             edge.labels = FALSE,#Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group, 
                             legend = FALSE, #This tells whether or not there is a legend
                             borders = TRUE, #This puts a border on each node when TRUE
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = 0.3)   #minimum = "sig", #Use either this (and the sampleSize line) or the minimum=0.2 (or whatever the threshold is)
                             #sampleSize = 8)
title(main = "Healthy Control Networks (r>0.3)", line =3)

#Setting minimum to .2
#Group with Major Depression
mdd_plot_p <- qgraph(mdd_mat_p, 
                             edge.labels = FALSE, #Labels edges with correlation values 
                             theme = "classic", #There are many themes. See ?qgraph
                             layout = "spring",  #There are many layouts. See ?qgraph
                             groups = group,
                            #graph = "pcor", #Zach says this "pcor" argument may be better than setting a minimum since it thresholds by significant correlations (I think)
                             #plot(1.5,0, type = "n"), #Or maybe this?
                             legend = FALSE, #("right", "(x,y)", pch=1, title= "right"), #or legend = FALSE
                             borders = TRUE,
                             overlay = TRUE, #This should to add a Venn diagram overlay ...but it doesn't seem to be working
                             colors = colors, #applies a customized list of colors
                             vsize = 2, #This changes the size of the vertices (nodes)
                             minimum = 0.2)
                             #sampleSize = 45) 
title(main = "Major Depression Networks (r>0.3)", line =3)



par(mfrow = c(1,2))
hc_plot_p
  title(main = "Healthy Control Networks (r>0.3)", line =3)
mdd_plot_p
  title(main = "Major Depression Networks (r>0.3)", line =3)

par(mfrow = c(1,3))
plot(hc2_plot_p)
  title(main = "HC Networks (r>0)", line =3)
plot(mdt_plot_p)
  title(main = "MDT Networks (r>0)", line =3)
plot(trd_plot_p)
  title(main = "TRD Networks (r>0)", line =3)

  
par(mfrow = c(1,1))
plot(sd_hc)
```


```{r}
#Taking the average of the matrices (without negative values):
mean_hc_p <- mean(hc_mat_p) 
std_hc_p <- SD(hc_mat_p)
stdev_hc_p <- mean(std_hc_p)

mean_mdd_p <-mean(mdd_mat_p) 
std_mdd_p <- SD(mdd_mat_p)
stdev_mdd_p <- mean(std_mdd_p)

######## t-test ########

t.test(hc_mat2_p,mdd_mat_p,alternative="two.sided",na.action=na.remove)



#Taking the averages & std. deviations of the entire matrices:
mean_hc2_p <- mean(hc_mat2_p)
std_hc2_p <- SD(hc_mat2_p)
stdev_hc2_p <- mean(std_hc2_p)

mean_mdt_p <- mean(mdt_mat_p)
std_mdt_p <- SD(mdt_mat_p)
stdev_mdt_p <- mean(std_mdt_p)

mean_trd_p <- mean(trd_mat_p)
std_trd_p <- SD(trd_mat_p)
stdev_trd_p <- mean(std_trd_p)

mean_hc_dm <- mean(hc_mat_dmode_p)
mean_mdd_dm <- mean(mdd_mat_dmode_p)

t_dmode <- t.test(hc_mat_dmode_p,mdd_mat_dmode_p,alternative="two.sided",na.action=na.remove)
summary(t_dmode)

mean_hc_fp <- mean(hc_mat_frparietal_p)
mean_mdd_fp <- mean(mdd_mat_frparietal_p)

t_fp <- t.test(hc_mat_frparietal_p,mdd_mat_frparietal_p,alternative="two.sided",na.action=na.remove)
summary(t_fp)


######## t-test ########
##I think these would actually need to be paired t-tests...so I need to change these to be correct:
hc_mdt_t <- t.test(hc_mat2_p,mdt_mat_p,alternative="two.sided",na.action=na.remove)
hc_mdt_t$p.value/3 < 0.05/3

hc_trd_t <- t.test(hc_mat2_p,trd_mat_p,alternative="two.sided",na.action=na.remove)
hc_trd_t$p.value/3 < 0.05/3

trd_mdt_t <- t.test(mdt_mat_p,trd_mat_p,alternative="two.sided",na.action=na.remove)
trd_mdt_t$p.value/3 < 0.05/3

pairwise.t.test()

############## ANOVA for means of 3 groups -- HC, MDT, TRD ###########
#Turn matrices into vectors:
hc2_p <- matrix(hc_mat2_p,dimnames=list(t(outer(colnames(hc_mat2_p),rownames(hc_mat2_p),FUN=paste)),NULL))
hc2_p1 <- cbind(group=1,hc2_p)

mdt_p <- matrix(mdt_mat_p,dimnames=list(t(outer(colnames(mdt_mat_p),rownames(mdt_mat_p),FUN=paste)),NULL))
mdt_p2 <- cbind(group=2,mdt_p)

trd_p <- matrix(trd_mat_p,dimnames=list(t(outer(colnames(trd_mat_p),rownames(trd_mat_p),FUN=paste)),NULL))
trd_p3 <- cbind(group=3,trd_p)

mat_p <- rbind(hc2_p1, mdt_p2, trd_p3)
mat_p_df <- data.frame(mat_p)

anova <- aov(V2~group, data = mat_p_df)
summary(anova)

#This isn't working for me:
#TukeyHSD(anova)

#This isn't working either...
#For Multiple Comparisons:
#library(multcomp)
#summary(glht(anova, linfct = mcp(group = "Tukey")))

pairwise.t.test(mat_p_df$V2, data$group,
                 p.adjust.method = "bonferroni")


#for the fpdm networks
mean_hc_fpdm2_p <- mean(hc_mat_fpdm2_p)

mean_mdt_fpdm_p <- mean(mdt_mat_fpdm_p)

mean_trd_fpdm_p <- mean(trd_mat_fpdm_p)


####################  Making a Table w/ overall FC ##################
tab_msd <- matrix(c((round(mean_hc_p,digits=4)),(round(stdev_hc_p,digits=4)), (round(mean_mdd_p,digits=4)), (round(stdev_mdd_p,digits=4)),"","",(round(mean_hc2_p,digits=4)),(round(stdev_hc2_p,digits=4)),(round(mean_mdt_p,digits=4)),(round(stdev_mdt_p,digits=4)),(round(mean_trd_p,digits=4)),(round(stdev_trd_p,digits=4))), ncol=2, byrow=TRUE)
colnames(tab_msd) <- c('Mean','S.D.')
rownames(tab_msd) <- c('HC','MDD','','HC','MDT','TRD')
write.table(tab_msd, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/fc.csv')

#tab_msd <- as.table(tab_msd)  #this is to visualize the table within R (I did this before writing it to a .csv file)
#tab_msd
```


```{r}
#For loop for creating igraph objects (used to write the next chunk):

matrix_ids <- c("hc_mat_p", "hc_mat_cingop_p", "hc_mat_dmode_p", "hc_mat_dorsalatt_p","hc_mat_fpdm_p", "hc_mat_frparietal_p","hc_mat_sali_p", "hc_mat_subc_p",

"hc_mat2_p", "hc_mat_cingop2_p", "hc_mat_dmode2_p", "hc_mat_dorsalatt2_p", "hc_mat_fpdm2_p", "hc_mat_frparietal2_p", "hc_mat_sali2_p", "hc_mat_subc2_p",

"mdd_mat_p", "mdd_mat_cingop_p", "mdd_mat_dmode_p", "mdd_mat_dorsalatt_p", "mdd_mat_fpdm_p", "mdd_mat_frparietal_p", "mdd_mat_sali_p", "mdd_mat_subc_p",

"mdt_mat_p", "mdt_mat_cingop_p", "mdt_mat_dmode_p", "mdt_mat_dorsalatt_p", "mdt_mat_fpdm_p", "mdt_mat_frparietal_p", "mdt_mat_sali_p", "mdt_mat_subc_p", 

"trd_mat_p", "trd_mat_cingop_p", "trd_mat_dmode_p", "trd_mat_dorsalatt_p", "trd_mat_fpdm_p", "trd_mat_frparietal_p", "trd_mat_sali_p", "trd_mat_subc_p")


for (id in matrix_ids) 
    {message <- paste("i_",id, "<- graph.adjacency(",id,", mode = 'undirected', weighted = TRUE))"
                  ) 
  
    print(message)}
```


Creating igraph object using "graph.adjacency" command. This is used to calculate graph theory metrics.
```{r}
#g <- graph.adjacency(hc_mat_p, mode = "undirected", weighted = TRUE)

i_hc_mat_p <- graph.adjacency( hc_mat_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_cingdm_p <- graph.adjacency( hc_mat_cingdm_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_cingop_p <- graph.adjacency( hc_mat_cingop_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_dmode_p <- graph.adjacency( hc_mat_dmode_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_dorsalatt_p <- graph.adjacency( hc_mat_dorsalatt_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_fpdm_p <- graph.adjacency( hc_mat_fpdm_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_frparietal_p <- graph.adjacency( hc_mat_frparietal_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_saldm_p <- graph.adjacency( hc_mat_saldm_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_sali_p <- graph.adjacency( hc_mat_sali_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_subc_p <- graph.adjacency( hc_mat_subc_p , mode = 'undirected', weighted = TRUE)

i_hc_mat2_p <- graph.adjacency( hc_mat2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_cingop2_p <- graph.adjacency( hc_mat_cingop2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_dmode2_p <- graph.adjacency( hc_mat_dmode2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_dorsalatt2_p <- graph.adjacency( hc_mat_dorsalatt2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_fpdm2_p <- graph.adjacency( hc_mat_fpdm2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_frparietal2_p <- graph.adjacency( hc_mat_frparietal2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_sali2_p <- graph.adjacency( hc_mat_sali2_p , mode = 'undirected', weighted = TRUE)
i_hc_mat_subc2_p <- graph.adjacency( hc_mat_subc2_p , mode = 'undirected', weighted = TRUE)

i_mdd_mat_p <- graph.adjacency( mdd_mat_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_cingdm_p <- graph.adjacency( mdd_mat_cingdm_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_cingop_p <- graph.adjacency( mdd_mat_cingop_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_dmode_p <- graph.adjacency( mdd_mat_dmode_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_dorsalatt_p <- graph.adjacency( mdd_mat_dorsalatt_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_fpdm_p <- graph.adjacency( mdd_mat_fpdm_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_frparietal_p <- graph.adjacency( mdd_mat_frparietal_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_saldm_p <- graph.adjacency( mdd_mat_saldm_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_sali_p <- graph.adjacency( mdd_mat_sali_p , mode = 'undirected', weighted = TRUE)
i_mdd_mat_subc_p <- graph.adjacency( mdd_mat_subc_p , mode = 'undirected', weighted = TRUE)

i_mdt_mat_p <- graph.adjacency( mdt_mat_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_cingop_p <- graph.adjacency( mdt_mat_cingop_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_dmode_p <- graph.adjacency( mdt_mat_dmode_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_dorsalatt_p <- graph.adjacency( mdt_mat_dorsalatt_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_fpdm_p <- graph.adjacency( mdt_mat_fpdm_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_frparietal_p <- graph.adjacency( mdt_mat_frparietal_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_sali_p <- graph.adjacency( mdt_mat_sali_p , mode = 'undirected', weighted = TRUE)
i_mdt_mat_subc_p <- graph.adjacency( mdt_mat_subc_p , mode = 'undirected', weighted = TRUE)

i_trd_mat_p <- graph.adjacency( trd_mat_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_cingop_p <- graph.adjacency( trd_mat_cingop_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_dmode_p <- graph.adjacency( trd_mat_dmode_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_dorsalatt_p <- graph.adjacency( trd_mat_dorsalatt_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_fpdm_p <- graph.adjacency( trd_mat_fpdm_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_frparietal_p <- graph.adjacency( trd_mat_frparietal_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_sali_p <- graph.adjacency( trd_mat_sali_p , mode = 'undirected', weighted = TRUE)
i_trd_mat_subc_p <- graph.adjacency( trd_mat_subc_p , mode = 'undirected', weighted = TRUE)

```


GLOBAL Metrics:
```{r}
#transitivity is sometimes also called the clustering coefficient. It measures the probability that 2 vertices (each adjacent to the main vertex) are connected
trans_hc <- transitivity(i_hc_mat_p)
trans_mdd <- transitivity(i_mdd_mat_p)

#library('fastnet')
#gcc_hc <- metric.cluster.global(i_hc_mat_p)  #This command gave the same answer as transitivity command in igraph



#Average path length (avg. # edges on shortest paths for all possible network node pairs)
pl_hc <- mean_distance(i_hc_mat_p, weights=NULL, unconnected=FALSE#, details = TRUE
                       )  #details gives a list with both the mean distance (res) and the number of unonneted erte pairs (if unconnected = TRUE, then only hte lengths of existing paths are averaged; if = FALSE, missing paths are considered to have infinite length --> mean distance becomes infinite too)
pl_mdd <-mean_distance(i_hc_mat_p, weights=NULL, unconnected=FALSE#, details = TRUE
                       )

#Mean degree (average degree of all nodes; degree = # edges connecting one node with other nodes)
d_hc <- degree(i_hc_mat_p)  # if you include v=V(graph) argument with v being the ids of specific vertices, then the degree will be calculated for particular vertices (i.e. those in a network)
md_hc <- mean(d_hc)

```

Global-level metrics (all calculations)
```{r}
trans_hc_mat<- transitivity(i_hc_mat_p)
                  dist_hc_mat <- distances(i_hc_mat_p, v=V(i_hc_mat_p), to=V(i_hc_mat_p)) 
                  pl_hc_mat <- mean_distance(i_hc_mat_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat <- degree(i_hc_mat_p)
                   md_hc_mat <- mean(d_hc_mat)

trans_mdd_mat<- transitivity(i_mdd_mat_p)
                  dist_mdd_mat <- distances(i_mdd_mat_p, v=V(i_mdd_mat_p), to=V(i_mdd_mat_p)) 
                   pl_mdd_mat <- mean_distance(i_mdd_mat_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat <- degree(i_mdd_mat_p)
                   md_mdd_mat <- mean(d_mdd_mat)

trans_hc_mat_cingdm<- transitivity(i_hc_mat_cingdm_p)
                  dist_hc_mat_cingdm <- distances(i_hc_mat_cingdm_p, v=V(i_hc_mat_cingdm_p), to=V(i_hc_mat_cingdm_p)) 
                  pl_hc_mat_cingdm <- mean_distance(i_hc_mat_cingdm_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_cingdm <- degree(i_hc_mat_cingdm_p)
                   md_hc_mat_cingdm <- mean(d_hc_mat_cingdm)
                   
trans_hc_mat_cingop<- transitivity(i_hc_mat_cingop_p)
                   dist_hc_mat_cingop <- distances(i_hc_mat_cingop_p, v=V(i_hc_mat_cingop_p), to=V(i_hc_mat_cingop_p)) 
                pl_hc_mat_cingop <- mean_distance(i_hc_mat_cingop_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_cingop <- degree(i_hc_mat_cingop_p)
                   md_hc_mat_cingop <- mean(d_hc_mat_cingop)

trans_hc_mat_dmode<- transitivity(i_hc_mat_dmode_p)
                   dist_hc_mat_dmode <- distances(i_hc_mat_dmode_p, v=V(i_hc_mat_dmode_p), to=V(i_hc_mat_dmode_p)) 
                   pl_hc_mat_dmode <- mean_distance(i_hc_mat_dmode_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_dmode <- degree(i_hc_mat_dmode_p)
                   md_hc_mat_dmode <- mean(d_hc_mat_dmode)

trans_hc_mat_dorsalatt<- transitivity(i_hc_mat_dorsalatt_p)
                   dist_hc_mat_dorsalatt <- distances(i_hc_mat_dorsalatt_p, v=V(i_hc_mat_dorsalatt_p), to=V(i_hc_mat_dorsalatt_p)) 
                   pl_hc_mat_dorsalatt <- mean_distance(i_hc_mat_dorsalatt_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_dorsalatt <- degree(i_hc_mat_dorsalatt_p)
                   md_hc_mat_dorsalatt <- mean(d_hc_mat_dorsalatt)

trans_hc_mat_fpdm<- transitivity(i_hc_mat_fpdm_p)
                   dist_hc_mat_fpdm <- distances(i_hc_mat_fpdm_p, v=V(i_hc_mat_fpdm_p), to=V(i_hc_mat_fpdm_p)) 
                   pl_hc_mat_fpdm <- mean_distance(i_hc_mat_fpdm_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_fpdm <- degree(i_hc_mat_fpdm_p)
                   md_hc_mat_fpdm <- mean(d_hc_mat_fpdm)

trans_hc_mat_frparietal<- transitivity(i_hc_mat_frparietal_p)
                   dist_hc_mat_frparietal <- distances(i_hc_mat_frparietal_p, v=V(i_hc_mat_frparietal_p), to=V(i_hc_mat_frparietal_p))
                   pl_hc_mat_frparietal <- mean_distance(i_hc_mat_frparietal_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_frparietal <- degree(i_hc_mat_frparietal_p)
                   md_hc_mat_frparietal <- mean(d_hc_mat_frparietal)

trans_hc_mat_saldm<- transitivity(i_hc_mat_saldm_p)
                   dist_hc_mat_saldm <- distances(i_hc_mat_saldm_p, v=V(i_hc_mat_saldm_p), to=V(i_hc_mat_saldm_p))
                   pl_hc_mat_saldm <- mean_distance(i_hc_mat_saldm_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_saldm <- degree(i_hc_mat_saldm_p)
                   md_hc_mat_saldm <- mean(d_hc_mat_saldm)
                   
trans_hc_mat_sali<- transitivity(i_hc_mat_sali_p)
                     dist_hc_mat_sali <- distances(i_hc_mat_sali_p, v=V(i_hc_mat_sali_p), to=V(i_hc_mat_sali_p))
                     pl_hc_mat_sali <- mean_distance(i_hc_mat_sali_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_sali <- degree(i_hc_mat_sali_p)
                   md_hc_mat_sali <- mean(d_hc_mat_sali)

trans_hc_mat_subc<- transitivity(i_hc_mat_subc_p)
                   dist_hc_mat_subc <- distances(i_hc_mat_subc_p, v=V(i_hc_mat_subc_p), to=V(i_hc_mat_subc_p))
                   pl_hc_mat_subc <- mean_distance(i_hc_mat_subc_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_subc <- degree(i_hc_mat_subc_p)
                   md_hc_mat_subc <- mean(d_hc_mat_subc)

trans_hc_mat2<- transitivity(i_hc_mat2_p)
                   pl_hc_mat2 <- mean_distance(i_hc_mat2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat2 <- degree(i_hc_mat2_p)
                   md_hc_mat2 <- mean(d_hc_mat2)

trans_hc_mat_cingop2<- transitivity(i_hc_mat_cingop2_p)
                   pl_hc_mat_cingop2 <- mean_distance(i_hc_mat_cingop2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_cingop2 <- degree(i_hc_mat_cingop2_p)
                   md_hc_mat_cingop2 <- mean(d_hc_mat_cingop2)

trans_hc_mat_dmode2<- transitivity(i_hc_mat_dmode2_p)
                   pl_hc_mat_dmode2 <- mean_distance(i_hc_mat_dmode2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_dmode2 <- degree(i_hc_mat_dmode2_p)
                   md_hc_mat_dmode2 <- mean(d_hc_mat_dmode2)

trans_hc_mat_dorsalatt2<- transitivity(i_hc_mat_dorsalatt2_p)
                   pl_hc_mat_dorsalatt2 <- mean_distance(i_hc_mat_dorsalatt2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_dorsalatt2 <- degree(i_hc_mat_dorsalatt2_p)
                   md_hc_mat_dorsalatt2 <- mean(d_hc_mat_dorsalatt2)

trans_hc_mat_fpdm2<- transitivity(i_hc_mat_fpdm2_p)
                   pl_hc_mat_fpdm2 <- mean_distance(i_hc_mat_fpdm2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_fpdm2 <- degree(i_hc_mat_fpdm2_p)
                   md_hc_mat_fpdm2 <- mean(d_hc_mat_fpdm2)

trans_hc_mat_frparietal2<- transitivity(i_hc_mat_frparietal2_p)
                   pl_hc_mat_frparietal2 <- mean_distance(i_hc_mat_frparietal2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_frparietal2 <- degree(i_hc_mat_frparietal2_p)
                   md_hc_mat_frparietal2 <- mean(d_hc_mat_frparietal2)

trans_hc_mat_sali2<- transitivity(i_hc_mat_sali2_p)
                   pl_hc_mat_sali2 <- mean_distance(i_hc_mat_sali2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_sali2 <- degree(i_hc_mat_sali2_p)
                   md_hc_mat_sali2 <- mean(d_hc_mat_sali2)

trans_hc_mat_subc2<- transitivity(i_hc_mat_subc2_p)
                   pl_hc_mat_subc2 <- mean_distance(i_hc_mat_subc2_p, weights=NULL, unconnected=FALSE)
                   d_hc_mat_subc2 <- degree(i_hc_mat_subc2_p)
                   md_hc_mat_subc2 <- mean(d_hc_mat_subc2)

trans_mdd_mat<- transitivity(i_mdd_mat_p)
                   dist_mdd_mat <- distances(i_mdd_mat_p, v=V(i_mdd_mat_p), to=V(i_mdd_mat_p))
                   pl_mdd_mat <- mean_distance(i_mdd_mat_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat <- degree(i_mdd_mat_p)
                   md_mdd_mat <- mean(d_mdd_mat)

trans_mdd_mat_cingdm<- transitivity(i_mdd_mat_cingdm_p)
                   dist_mdd_mat_cingdm <- distances(i_mdd_mat_cingdm_p, v=V(i_mdd_mat_cingdm_p), to=V(i_mdd_mat_cingdm_p))
                   pl_mdd_mat_cingdm <- mean_distance(i_mdd_mat_cingdm_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_cingdm <- degree(i_mdd_mat_cingdm_p)
                   md_mdd_mat_cingdm <- mean(d_mdd_mat_cingdm)
                
trans_mdd_mat_cingop<- transitivity(i_mdd_mat_cingop_p)
                  dist_mdd_mat_cingop <- distances(i_mdd_mat_cingop_p, v=V(i_mdd_mat_cingop_p), to=V(i_mdd_mat_cingop_p)) 
                  pl_mdd_mat_cingop <- mean_distance(i_mdd_mat_cingop_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_cingop <- degree(i_mdd_mat_cingop_p)
                   md_mdd_mat_cingop <- mean(d_mdd_mat_cingop)

trans_mdd_mat_dmode<- transitivity(i_mdd_mat_dmode_p)
                   dist_mdd_mat_dmode <- distances(i_mdd_mat_dmode_p, v=V(i_mdd_mat_dmode_p), to=V(i_mdd_mat_dmode_p))  
                   pl_mdd_mat_dmode <- mean_distance(i_mdd_mat_dmode_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_dmode <- degree(i_mdd_mat_dmode_p)
                   md_mdd_mat_dmode <- mean(d_mdd_mat_dmode)

trans_mdd_mat_dorsalatt<- transitivity(i_mdd_mat_dorsalatt_p)
                   dist_mdd_mat_dorsalatt <- distances(i_mdd_mat_dorsalatt_p, v=V(i_mdd_mat_dorsalatt_p), to=V(i_mdd_mat_dorsalatt_p))  
                   pl_mdd_mat_dorsalatt <- mean_distance(i_mdd_mat_dorsalatt_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_dorsalatt <- degree(i_mdd_mat_dorsalatt_p)
                   md_mdd_mat_dorsalatt <- mean(d_mdd_mat_dorsalatt)

trans_mdd_mat_fpdm<- transitivity(i_mdd_mat_fpdm_p)
                   dist_mdd_mat_fpdm <- distances(i_mdd_mat_fpdm_p, v=V(i_mdd_mat_fpdm_p), to=V(i_mdd_mat_fpdm_p))  
                   pl_mdd_mat_fpdm <- mean_distance(i_mdd_mat_fpdm_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_fpdm <- degree(i_mdd_mat_fpdm_p)
                   md_mdd_mat_fpdm <- mean(d_mdd_mat_fpdm)

trans_mdd_mat_frparietal<- transitivity(i_mdd_mat_frparietal_p)
                   dist_mdd_mat_frparietal <- distances(i_mdd_mat_frparietal_p, v=V(i_mdd_mat_frparietal_p), to=V(i_mdd_mat_frparietal_p))   
                   pl_mdd_mat_frparietal <- mean_distance(i_mdd_mat_frparietal_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_frparietal <- degree(i_mdd_mat_frparietal_p)
                   md_mdd_mat_frparietal <- mean(d_mdd_mat_frparietal)

trans_mdd_mat_saldm<- transitivity(i_mdd_mat_saldm_p)
                   dist_mdd_mat_saldm <- distances(i_mdd_mat_saldm_p, v=V(i_mdd_mat_saldm_p), to=V(i_mdd_mat_saldm_p))   
                   pl_mdd_mat_saldm <- mean_distance(i_mdd_mat_saldm_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_saldm <- degree(i_mdd_mat_saldm_p)
                   md_mdd_mat_saldm <- mean(d_mdd_mat_saldm)
                   
trans_mdd_mat_sali<- transitivity(i_mdd_mat_sali_p)
                    dist_mdd_mat_sali <- distances(i_mdd_mat_sali_p, v=V(i_mdd_mat_sali_p), to=V(i_mdd_mat_sali_p))  
                    pl_mdd_mat_sali <- mean_distance(i_mdd_mat_sali_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_sali <- degree(i_mdd_mat_sali_p)
                   md_mdd_mat_sali <- mean(d_mdd_mat_sali)

trans_mdd_mat_subc<- transitivity(i_mdd_mat_subc_p)
                   dist_mdd_mat_subc <- distances(i_mdd_mat_subc_p, v=V(i_mdd_mat_subc_p), to=V(i_mdd_mat_subc_p))  
                  pl_mdd_mat_subc <- mean_distance(i_mdd_mat_subc_p, weights=NULL, unconnected=FALSE)
                   d_mdd_mat_subc <- degree(i_mdd_mat_subc_p)
                   md_mdd_mat_subc <- mean(d_mdd_mat_subc)

trans_mdt_mat<- transitivity(i_mdt_mat_p)
                   pl_mdt_mat <- mean_distance(i_mdt_mat_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat <- degree(i_mdt_mat_p)
                   md_mdt_mat <- mean(d_mdt_mat)

trans_mdt_mat_cingop<- transitivity(i_mdt_mat_cingop_p)
                   pl_mdt_mat_cingop <- mean_distance(i_mdt_mat_cingop_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_cingop <- degree(i_mdt_mat_cingop_p)
                   md_mdt_mat_cingop <- mean(d_mdt_mat_cingop)

trans_mdt_mat_dmode<- transitivity(i_mdt_mat_dmode_p)
                   pl_mdt_mat_dmode <- mean_distance(i_mdt_mat_dmode_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_dmode <- degree(i_mdt_mat_dmode_p)
                   md_mdt_mat_dmode <- mean(d_mdt_mat_dmode)

trans_mdt_mat_dorsalatt<- transitivity(i_mdt_mat_dorsalatt_p)
                   pl_mdt_mat_dorsalatt <- mean_distance(i_mdt_mat_dorsalatt_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_dorsalatt <- degree(i_mdt_mat_dorsalatt_p)
                   md_mdt_mat_dorsalatt <- mean(d_mdt_mat_dorsalatt)

trans_mdt_mat_fpdm<- transitivity(i_mdt_mat_fpdm_p)
                   pl_mdt_mat_fpdm <- mean_distance(i_mdt_mat_fpdm_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_fpdm <- degree(i_mdt_mat_fpdm_p)
                   md_mdt_mat_fpdm <- mean(d_mdt_mat_fpdm)

trans_mdt_mat_frparietal<- transitivity(i_mdt_mat_frparietal_p)
                   pl_mdt_mat_frparietal <- mean_distance(i_mdt_mat_frparietal_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_frparietal <- degree(i_mdt_mat_frparietal_p)
                   md_mdt_mat_frparietal <- mean(d_mdt_mat_frparietal)

trans_mdt_mat_sali<- transitivity(i_mdt_mat_sali_p)
                   pl_mdt_mat_sali <- mean_distance(i_mdt_mat_sali_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_sali <- degree(i_mdt_mat_sali_p)
                   md_mdt_mat_sali <- mean(d_mdt_mat_sali)

trans_mdt_mat_subc<- transitivity(i_mdt_mat_subc_p)
                   pl_mdt_mat_subc <- mean_distance(i_mdt_mat_subc_p, weights=NULL, unconnected=FALSE)
                   d_mdt_mat_subc <- degree(i_mdt_mat_subc_p)
                   md_mdt_mat_subc <- mean(d_mdt_mat_subc)

trans_trd_mat<- transitivity(i_trd_mat_p)
                   pl_trd_mat <- mean_distance(i_trd_mat_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat <- degree(i_trd_mat_p)
                   md_trd_mat <- mean(d_trd_mat)

trans_trd_mat_cingop<- transitivity(i_trd_mat_cingop_p)
                   pl_trd_mat_cingop <- mean_distance(i_trd_mat_cingop_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_cingop <- degree(i_trd_mat_cingop_p)
                   md_trd_mat_cingop <- mean(d_trd_mat_cingop)

trans_trd_mat_dmode<- transitivity(i_trd_mat_dmode_p)
                   pl_trd_mat_dmode <- mean_distance(i_trd_mat_dmode_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_dmode <- degree(i_trd_mat_dmode_p)
                   md_trd_mat_dmode <- mean(d_trd_mat_dmode)

trans_trd_mat_dorsalatt<- transitivity(i_trd_mat_dorsalatt_p)
                   pl_trd_mat_dorsalatt <- mean_distance(i_trd_mat_dorsalatt_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_dorsalatt <- degree(i_trd_mat_dorsalatt_p)
                   md_trd_mat_dorsalatt <- mean(d_trd_mat_dorsalatt)

trans_trd_mat_fpdm<- transitivity(i_trd_mat_fpdm_p)
                   pl_trd_mat_fpdm <- mean_distance(i_trd_mat_fpdm_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_fpdm <- degree(i_trd_mat_fpdm_p)
                   md_trd_mat_fpdm <- mean(d_trd_mat_fpdm)

trans_trd_mat_frparietal<- transitivity(i_trd_mat_frparietal_p)
                   pl_trd_mat_frparietal <- mean_distance(i_trd_mat_frparietal_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_frparietal <- degree(i_trd_mat_frparietal_p)
                   md_trd_mat_frparietal <- mean(d_trd_mat_frparietal)

trans_trd_mat_sali<- transitivity(i_trd_mat_sali_p)
                   pl_trd_mat_sali <- mean_distance(i_trd_mat_sali_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_sali <- degree(i_trd_mat_sali_p)
                   md_trd_mat_sali <- mean(d_trd_mat_sali)

trans_trd_mat_subc<- transitivity(i_trd_mat_subc_p)
                   pl_trd_mat_subc <- mean_distance(i_trd_mat_subc_p, weights=NULL, unconnected=FALSE)
                   d_trd_mat_subc <- degree(i_trd_mat_subc_p)
                   md_trd_mat_subc <- mean(d_trd_mat_subc)

                                      
####################  t-tests for Global Metrics ####################
t_trans <- t.test(trans_hc_mat,trans_mdd_mat,alternative="two.sided",na.action=na.remove)

t_trans_cingdm <- t.test(trans_hc_mat_cingdm,trans_mdd_mat_cingdm,alternative="two.sided",na.action=na.remove)
                                      
t_trans_cingop <- t.test(trans_hc_mat_cingop,trans_mdd_mat_cingop,alternative="two.sided",na.action=na.remove)

t_trans_dmode <- t.test(trans_hc_mat_dmode,trans_mdd_mat_dmode,alternative="two.sided",na.action=na.remove)

t_trans_dorsalatt <- t.test(trans_hc_mat_dorsalatt,trans_mdd_mat_dorsalatt,alternative="two.sided",na.action=na.remove)

t_trans_fpdm <- t.test(trans_hc_mat_fpdm,trans_mdd_mat_fpdm,alternative="two.sided",na.action=na.remove)

t_trans_frparietal <- t.test(trans_hc_mat_frparietal,trans_mdd_mat_frparietal,alternative="two.sided",na.action=na.remove)

t_trans_saldm <- t.test(trans_hc_mat_saldm,trans_mdd_mat_saldm,alternative="two.sided",na.action=na.remove)

t_trans_sali <- t.test(trans_hc_mat_sali,trans_mdd_mat_sali,alternative="two.sided",na.action=na.remove)

t_trans_subc <- t.test(trans_hc_mat_subc,trans_mdd_mat_subc,alternative="two.sided",na.action=na.remove)
#
t_pl <- t.test(dist_hc_mat,dist_mdd_mat,alternative="two.sided",na.action=na.remove)

t_pl_cingdm <- t.test(dist_hc_mat_cingdm,dist_mdd_mat_cingdm,alternative="two.sided",na.action=na.remove)

t_pl_cingop <- t.test(dist_hc_mat_cingop,dist_mdd_mat_cingop,alternative="two.sided",na.action=na.remove)

t_pl_dmode <- t.test(dist_hc_mat_dmode,dist_mdd_mat_dmode,alternative="two.sided",na.action=na.remove)

t_pl_dorsalatt <- t.test(dist_hc_mat_dorsalatt,dist_mdd_mat_dorsalatt,alternative="two.sided",na.action=na.remove)

t_pl_fpdm <- t.test(dist_hc_mat_fpdm,dist_mdd_mat_fpdm,alternative="two.sided",na.action=na.remove)
             
t_pl_frparietal <- t.test(dist_hc_mat_frparietal,dist_mdd_mat_frparietal,alternative="two.sided",na.action=na.remove)

t_pl_saldm <- t.test(dist_hc_mat_saldm,dist_mdd_mat_saldm,alternative="two.sided",na.action=na.remove)

t_pl_sali <- t.test(dist_hc_mat_sali,dist_mdd_mat_sali,alternative="two.sided",na.action=na.remove)

t_pl_subc <- t.test(dist_hc_mat_subc,dist_mdd_mat_subc,alternative="two.sided",na.action=na.remove)
#
t_md <- t.test(d_hc_mat,d_mdd_mat,alternative="two.sided",na.action=na.remove)
t_md$p.value

t_md_cingdm <- t.test(d_hc_mat_cingdm,d_mdd_mat_cingdm,alternative="two.sided",na.action=na.remove)
t_md_cingop$p.value

t_md_cingop <- t.test(d_hc_mat_cingop,d_mdd_mat_cingop,alternative="two.sided",na.action=na.remove)
t_md_cingop$p.value

t_md_dmode <- t.test(d_hc_mat_dmode,d_mdd_mat_dmode,alternative="two.sided",na.action=na.remove)
t_md_dmode$p.value

t_md_dorsalatt <- t.test(d_hc_mat_dorsalatt,d_mdd_mat_dorsalatt,alternative="two.sided",na.action=na.remove)
t_md_dorsalatt$p.value

t_md_fpdm <- t.test(d_hc_mat_fpdm,d_mdd_mat_fpdm,alternative="two.sided",na.action=na.remove)
t_md_fpdm$p.value

t_md_frparietal <- t.test(d_hc_mat_frparietal,d_mdd_mat_frparietal,alternative="two.sided",na.action=na.remove)
t_md_frparietal$p.value

t_md_saldm <- t.test(d_hc_mat_saldm,d_mdd_mat_saldm,alternative="two.sided",na.action=na.remove)
t_pl_saldm$p.value

t_md_sali <- t.test(d_hc_mat_sali,d_mdd_mat_sali,alternative="two.sided",na.action=na.remove)
t_md_sali$p.value

t_md_subc <- t.test(d_hc_mat_subc,d_mdd_mat_subc,alternative="two.sided",na.action=na.remove)
t_md_subc$p.value

#############  Making a Table w/ overall Global Metrics #############
tab_global <- matrix(c(trans_hc_mat,pl_hc_mat,md_hc_mat,t_md$p.value,trans_mdd_mat, pl_mdd_mat, md_mdd_mat, t_md$p.value,
                       trans_hc_mat_cingdm,pl_hc_mat_cingdm,md_hc_mat_cingdm,t_md_cingdm$p.value,trans_mdd_mat_cingdm, pl_mdd_mat_cingdm, md_mdd_mat_cingdm, t_md_cingdm$p.value,
                       trans_hc_mat_cingop,pl_hc_mat_cingop,md_hc_mat_cingop,t_md_cingop$p.value,trans_mdd_mat_cingop, pl_mdd_mat_cingop, md_mdd_mat_cingop, t_md_cingop$p.value,
                       trans_hc_mat_dmode,pl_hc_mat_dmode,md_hc_mat_dmode,t_md_dmode$p.value,trans_mdd_mat_dmode, pl_mdd_mat_dmode, md_mdd_mat_dmode, t_md_dmode$p.value,
                       trans_hc_mat_dorsalatt,pl_hc_mat_dorsalatt,md_hc_mat_dorsalatt,t_md_dorsalatt$p.value,trans_mdd_mat_dorsalatt, pl_mdd_mat_dorsalatt, md_mdd_mat_dorsalatt, t_md_dorsalatt$p.value,
                       trans_hc_mat_fpdm,pl_hc_mat_fpdm,md_hc_mat_fpdm,t_md_fpdm$p.value,trans_mdd_mat_fpdm, pl_mdd_mat_fpdm, md_mdd_mat_fpdm, t_md_fpdm$p.value,
                       trans_hc_mat_frparietal,pl_hc_mat_frparietal,md_hc_mat_frparietal,t_md_frparietal$p.value,trans_mdd_mat_frparietal, pl_mdd_mat_frparietal, md_mdd_mat_frparietal, t_md_frparietal$p.value,
                       
                       trans_hc_mat_sali,pl_hc_mat_sali,md_hc_mat_sali,t_md_sali$p.value,trans_mdd_mat_sali, pl_mdd_mat_sali, md_mdd_mat_sali, t_md_sali$p.value,
                       trans_hc_mat_subc,pl_hc_mat_subc,md_hc_mat_subc,t_md_subc$p.value,trans_mdd_mat_subc, pl_mdd_mat_subc, md_mdd_mat_subc, t_md_subc$p.value
                       ), ncol=4, byrow=TRUE)
colnames(tab_global) <- c('transitivity','average path length','mean degree','mean degree p-value')
rownames(tab_global) <- c('HC','MDD','HC cingdm','MDD cingdm','HC cingop', 'MDD cingop', 'HC DMN', 'MDD DMN', 'HC dorsalatt', 'MDD dorsalatt', 'HC fpdm', 'MDD fpdm', 'HC frparietal', 'MDD frparietal', 'HC sali', 'MDD sali', 'HC subc', 'MDD subc')
write.table(tab_global, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/global.csv')


#p-value for path length
tab_global_p_pl <- matrix(c(t_pl$p.value,
                       t_pl_cingdm$p.value,
                       t_pl_cingop$p.value,
                       t_pl_dmode$p.value,
                       t_pl_dorsalatt$p.value,
                       t_pl_fpdm$p.value,
                       t_pl_frparietal$p.value,
                       t_pl_sali$p.value,
                       t_pl_saldm$p.value,
                       t_pl_subc$p.value
                       ), ncol=1, byrow=TRUE)
colnames(tab_global_p_pl) <- c('average path length p-value')
rownames(tab_global_p_pl) <- c('HC/MDD','HC cingdm/MDD cingdm','HC cingop/MDD cingop', 'HC DMN/MDD DMN', 'HC dorsalatt/MDD dorsalatt', 'HC fpdm/MDD fpdm', 'HC frparietal/MDD frparietal','HC saldm/MDD saldm', 'HC sali/MDD sali', 'HC subc/MDD subc')
write.table(tab_global_p_pl, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/global_t_test_pl.csv')



tab_global_p_saldm <- matrix(c(t_pl_saldm$p.value
                                         ), ncol=1, byrow=TRUE)
colnames(tab_global_p_saldm) <- c('average path length p-value')
rownames(tab_global_p_saldm) <- c('HC saldm/MDD saldm')
write.table(tab_global_p_saldm, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/t_saldm.csv')
t_pl_saldm
```



Middle-level (modular) metrics:
```{r}
#modularity

#Modularity score - higher score means more modular
#Modularity of a community structure of a graph.This function calculates how modular is a given division of a graph into subgraphs
groupvector <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,
                 2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,
                 3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,
                 4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,
                 5,5,5,5,5,5,5,5,5,5,5,5,5,
                 6,6,6,6,6,6,6,6,6,6,6)  #1 = cingop, 2=dm, 3=fp, 4=sali, 5=subc, 6=dorsalatt
  #class(groupvector) #checks that the vector is numeric (numeric class is required for the modularity function)
  #length(groupvector) #checks how long the vector is
mod_hc <- modularity(i_hc_mat_p, membership=groupvector, weights=NULL, resolution=1)
mod_mdd <- modularity(i_mdd_mat_p, membership=groupvector, weights=NULL, resolution=1)

#this is not working to find the modularity of cingop network itself:
#cingopvector <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1)
#mod_cingop <- modularity(i_hc_mat_cingop_p, membership=groupvector, weights=NULL, resolution=1)


##################### Creating data-driven Communities within networks #######################
wt_hc_dmode <- cluster_walktrap(i_hc_mat_dmode_p, weights=NULL, steps=4) #an earlier online version describing walktrap in igraph suggests using 4-5 steps and that 3-8 steps usually works
    
wt_mdd_dmode <- cluster_walktrap(i_mdd_mat_dmode_p, weights=NULL, steps=4)


#################### Turning communities into numeric vectors ########################
member_hc_dmode <- membership(wt_hc_dmode)
member_mdd_dmode <- membership(wt_mdd_dmode)


################### Computing modularity scores for wt-derived communities ###################
mod_hc_dmode <- modularity(i_hc_mat_dmode_p, membership=member_hc_dmode, weights=NULL, resolution=1)

#Computing modularity of MDD dmode based on hc-derived communities:
mod_mdd_dmode2 <- modularity(i_mdd_mat_dmode_p, membership=member_hc_dmode, weights=NULL, resolution=1)

#Computing modularity of hc dmode based on MDD-derived communities:
mod_hc_dmode2 <- modularity(i_hc_mat_dmode_p, membership=member_mdd_dmode, weights=NULL, resolution=1)


###### ALL THE NETWORKS == MODULARITY ######
wt_hc_mat_cingop<- cluster_walktrap(i_hc_mat_cingop_p, weights=NULL, steps=4)
                   member_hc_mat_cingop <- membership(wt_hc_mat_cingop)
                   mod_hc_mat_cingop <- modularity(i_hc_mat_cingop_p, membership=member_hc_mat_cingop, weights=NULL, resolution=1)

wt_hc_mat_dmode<- cluster_walktrap(i_hc_mat_dmode_p, weights=NULL, steps=4)
                   member_hc_mat_dmode <- membership(wt_hc_mat_dmode)
                   mod_hc_mat_dmode <- modularity(i_hc_mat_dmode_p, membership=member_hc_mat_dmode, weights=NULL, resolution=1)

wt_hc_mat_dorsalatt<- cluster_walktrap(i_hc_mat_dorsalatt_p, weights=NULL, steps=4)
                   member_hc_mat_dorsalatt <- membership(wt_hc_mat_dorsalatt)
                   mod_hc_mat_dorsalatt <- modularity(i_hc_mat_dorsalatt_p, membership=member_hc_mat_dorsalatt, weights=NULL, resolution=1)

wt_hc_mat_frparietal<- cluster_walktrap(i_hc_mat_frparietal_p, weights=NULL, steps=4)
                   member_hc_mat_frparietal <- membership(wt_hc_mat_frparietal)
                   mod_hc_mat_frparietal <- modularity(i_hc_mat_frparietal_p, membership=member_hc_mat_frparietal, weights=NULL, resolution=1)

wt_hc_mat_sali<- cluster_walktrap(i_hc_mat_sali_p, weights=NULL, steps=4)
                   member_hc_mat_sali <- membership(wt_hc_mat_sali)
                   mod_hc_mat_sali <- modularity(i_hc_mat_sali_p, membership=member_hc_mat_sali, weights=NULL, resolution=1)

wt_hc_mat_subc<- cluster_walktrap(i_hc_mat_subc_p, weights=NULL, steps=4)
                   member_hc_mat_subc <- membership(wt_hc_mat_subc)
                   mod_hc_mat_subc <- modularity(i_hc_mat_subc_p, membership=member_hc_mat_subc, weights=NULL, resolution=1)

wt_mdd_mat_cingop<- cluster_walktrap(i_mdd_mat_cingop_p, weights=NULL, steps=4)
                   member_mdd_mat_cingop <- membership(wt_mdd_mat_cingop)
                   mod_mdd_mat_cingop <- modularity(i_mdd_mat_cingop_p, membership=member_mdd_mat_cingop, weights=NULL, resolution=1)

wt_mdd_mat_dmode<- cluster_walktrap(i_mdd_mat_dmode_p, weights=NULL, steps=4)
                   member_mdd_mat_dmode <- membership(wt_mdd_mat_dmode)
                   mod_mdd_mat_dmode <- modularity(i_mdd_mat_dmode_p, membership=member_mdd_mat_dmode, weights=NULL, resolution=1)

wt_mdd_mat_dorsalatt<- cluster_walktrap(i_mdd_mat_dorsalatt_p, weights=NULL, steps=4)
                   member_mdd_mat_dorsalatt <- membership(wt_mdd_mat_dorsalatt)
                   mod_mdd_mat_dorsalatt <- modularity(i_mdd_mat_dorsalatt_p, membership=member_mdd_mat_dorsalatt, weights=NULL, resolution=1)

wt_mdd_mat_frparietal<- cluster_walktrap(i_mdd_mat_frparietal_p, weights=NULL, steps=4)
                   member_mdd_mat_frparietal <- membership(wt_mdd_mat_frparietal)
                   mod_mdd_mat_frparietal <- modularity(i_mdd_mat_frparietal_p, membership=member_mdd_mat_frparietal, weights=NULL, resolution=1)

wt_mdd_mat_sali<- cluster_walktrap(i_mdd_mat_sali_p, weights=NULL, steps=4)
                   member_mdd_mat_sali <- membership(wt_mdd_mat_sali)
                   mod_mdd_mat_sali <- modularity(i_mdd_mat_sali_p, membership=member_mdd_mat_sali, weights=NULL, resolution=1)

wt_mdd_mat_subc<- cluster_walktrap(i_mdd_mat_subc_p, weights=NULL, steps=4)
                   member_mdd_mat_subc <- membership(wt_mdd_mat_subc)
                   mod_mdd_mat_subc <- modularity(i_mdd_mat_subc_p, membership=member_mdd_mat_subc, weights=NULL, resolution=1)


```


```{r}
############## Creating a table for Modularity ################
tab_mod <- matrix(c(mod_hc,mod_mdd,
                    
                       mod_hc_mat_cingop,
                       mod_mdd_mat_cingop,
                       mod_hc_mat_dmode,
                       mod_mdd_mat_dmode,
                       mod_hc_mat_dorsalatt,
                       mod_mdd_mat_dorsalatt,
                       mod_hc_mat_frparietal,
                       mod_mdd_mat_frparietal,
                       mod_hc_mat_sali,
                       mod_mdd_mat_sali,
                       mod_hc_mat_subc,
                       mod_mdd_mat_subc
                       ), ncol=1, byrow=TRUE)
colnames(tab_mod) <- c('modularity')
rownames(tab_mod) <- c('HC','MDD','HC cingop','MDD cingop', 'HC DMN','MDD DMN', 'HC dorsalatt','MDD dorsalatt', 'HC frparietal','MDD frparietal', 'HC sali','MDD sali', 'HC subc','MDD subc')
write.table(tab_mod, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/modularity.csv')


```


LOCAL Metrics
```{r}
#Degree  #Counts the number of edges connecting one node with others

deg_hc <- degree(i_hc_mat_p,v = V(i_hc_mat_p))
deg_mdd <- degree(i_mdd_mat_p ,v = V(i_mdd_mat_p))


deg_hc_mat_cingdm<- degree(i_hc_mat_cingdm_p, v = V(i_hc_mat_cingdm_p))
                   btw_hc_mat_cingdm <- betweenness(i_hc_mat_cingdm_p, v = V(i_hc_mat_cingdm_p))

deg_hc_mat_cingop<- degree(i_hc_mat_cingop_p, v = V(i_hc_mat_cingop_p))
                   btw_hc_mat_cingop <- betweenness(i_hc_mat_cingop_p, v = V(i_hc_mat_cingop_p))

deg_hc_mat_dmode<- degree(i_hc_mat_dmode_p, v = V(i_hc_mat_dmode_p))
                   btw_hc_mat_dmode <- betweenness(i_hc_mat_dmode_p, v = V(i_hc_mat_dmode_p))

deg_hc_mat_dorsalatt<- degree(i_hc_mat_dorsalatt_p, v = V(i_hc_mat_dorsalatt_p))
                   btw_hc_mat_dorsalatt <- betweenness(i_hc_mat_dorsalatt_p, v = V(i_hc_mat_dorsalatt_p))

deg_hc_mat_fpdm<- degree(i_hc_mat_fpdm_p, v = V(i_hc_mat_fpdm_p))
                   btw_hc_mat_fpdm <- betweenness(i_hc_mat_fpdm_p, v = V(i_hc_mat_fpdm_p))

deg_hc_mat_frparietal<- degree(i_hc_mat_frparietal_p, v = V(i_hc_mat_frparietal_p))
                   btw_hc_mat_frparietal <- betweenness(i_hc_mat_frparietal_p, v = V(i_hc_mat_frparietal_p))

deg_hc_mat_saldm<- degree(i_hc_mat_saldm_p, v = V(i_hc_mat_saldm_p))
                   btw_hc_mat_saldm <- betweenness(i_hc_mat_saldm_p, v = V(i_hc_mat_saldm_p))

deg_hc_mat_sali<- degree(i_hc_mat_sali_p, v = V(i_hc_mat_sali_p))
                   btw_hc_mat_sali <- betweenness(i_hc_mat_sali_p, v = V(i_hc_mat_sali_p))

deg_hc_mat_subc<- degree(i_hc_mat_subc_p, v = V(i_hc_mat_subc_p))
                   btw_hc_mat_subc <- betweenness(i_hc_mat_subc_p, v = V(i_hc_mat_subc_p))


deg_mdd_mat_cingdm<- degree(i_mdd_mat_cingdm_p, v = V(i_mdd_mat_cingdm_p))
                   btw_mdd_mat_cingdm <- betweenness(i_mdd_mat_cingdm_p, v = V(i_mdd_mat_cingdm_p))
                                      
deg_mdd_mat_cingop<- degree(i_mdd_mat_cingop_p, v = V(i_mdd_mat_cingop_p))
                   btw_mdd_mat_cingop <- betweenness(i_mdd_mat_cingop_p, v = V(i_mdd_mat_cingop_p))

deg_mdd_mat_dmode<- degree(i_mdd_mat_dmode_p, v = V(i_mdd_mat_dmode_p))
                   btw_mdd_mat_dmode <- betweenness(i_mdd_mat_dmode_p, v = V(i_mdd_mat_dmode_p))

deg_mdd_mat_dorsalatt<- degree(i_mdd_mat_dorsalatt_p, v = V(i_mdd_mat_dorsalatt_p))
                   btw_mdd_mat_dorsalatt <- betweenness(i_mdd_mat_dorsalatt_p, v = V(i_mdd_mat_dorsalatt_p))

deg_mdd_mat_fpdm<- degree(i_mdd_mat_fpdm_p, v = V(i_mdd_mat_fpdm_p))
                   btw_mdd_mat_fpdm <- betweenness(i_mdd_mat_fpdm_p, v = V(i_mdd_mat_fpdm_p))

deg_mdd_mat_frparietal<- degree(i_mdd_mat_frparietal_p, v = V(i_mdd_mat_frparietal_p))
                   btw_mdd_mat_frparietal <- betweenness(i_mdd_mat_frparietal_p, v = V(i_mdd_mat_frparietal_p))

deg_mdd_mat_saldm<- degree(i_mdd_mat_saldm_p, v = V(i_mdd_mat_saldm_p))
                   btw_mdd_mat_saldm <- betweenness(i_mdd_mat_saldm_p, v = V(i_mdd_mat_saldm_p))

deg_mdd_mat_sali<- degree(i_mdd_mat_sali_p, v = V(i_mdd_mat_sali_p))
                   btw_mdd_mat_sali <- betweenness(i_mdd_mat_sali_p, v = V(i_mdd_mat_sali_p))

deg_mdd_mat_subc<- degree(i_mdd_mat_subc_p, v = V(i_mdd_mat_subc_p))
                   btw_mdd_mat_subc <- betweenness(i_mdd_mat_subc_p, v = V(i_mdd_mat_subc_p))

                   
#mean betweenness:
mb_hc<- mean(btw_hc)

mb_mdd<- mean(btw_mdd)

mb_hc_mat_cingdm<- mean(btw_hc_mat_cingdm)

mb_hc_mat_cingop<- mean(btw_hc_mat_cingop)

mb_hc_mat_dmode<- mean(btw_hc_mat_dmode)

mb_hc_mat_dorsalatt<- mean(btw_hc_mat_dorsalatt)

mb_hc_mat_fpdm<- mean(btw_hc_mat_fpdm)

mb_hc_mat_frparietal<- mean(btw_hc_mat_frparietal)

mb_hc_mat_saldm<- mean(btw_hc_mat_saldm)

mb_hc_mat_sali<- mean(btw_hc_mat_sali)

mb_hc_mat_subc<- mean(btw_hc_mat_subc)

mb_mdd_mat<- mean(btw_mdd_mat)

mb_mdd_mat_cingdm<- mean(btw_mdd_mat_cingdm)

mb_mdd_mat_cingop<- mean(btw_mdd_mat_cingop)

mb_mdd_mat_dmode<- mean(btw_mdd_mat_dmode)

mb_mdd_mat_dorsalatt<- mean(btw_mdd_mat_dorsalatt)

mb_mdd_mat_fpdm<- mean(btw_mdd_mat_fpdm)

mb_mdd_mat_frparietal<- mean(btw_mdd_mat_frparietal)

mb_mdd_mat_saldm<- mean(btw_mdd_mat_saldm)

mb_mdd_mat_sali<- mean(btw_mdd_mat_sali)

mb_mdd_mat_subc<- mean(btw_mdd_mat_subc)

                    
#t-tests for degree & betweenness:
t_deg <- t.test(deg_hc,deg_mdd,alternative="two.sided",na.action=na.remove)
t_deg$p.value

t_btw <- t.test(btw_hc,btw_mdd,alternative="two.sided",na.action=na.remove)
t_btw$p.value
                   

t_btw__mat_cingop<- t.test(btw_hc_mat_cingop,btw_mdd_mat_cingop, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_cingop$p.value
                   t_deg__mat_cingop <- t.test(deg_hc_mat_cingop,deg_mdd_mat_cingop,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_cingop$p.value

t_btw__mat_cingdm<- t.test(btw_hc_mat_cingdm,btw_mdd_mat_cingdm, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_cingdm$p.value
                   t_deg__mat_cingdm <- t.test(deg_hc_mat_cingdm,deg_mdd_mat_cingdm,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_cingdm$p.value

t_btw__mat_dmode<- t.test(btw_hc_mat_dmode,btw_mdd_mat_dmode, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_dmode$p.value
                   t_deg__mat_dmode <- t.test(deg_hc_mat_dmode,deg_mdd_mat_dmode,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_dmode$p.value

t_btw__mat_dorsalatt<- t.test(btw_hc_mat_dorsalatt,btw_mdd_mat_dorsalatt, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_dorsalatt$p.value
                   t_deg__mat_dorsalatt <- t.test(deg_hc_mat_dorsalatt,deg_mdd_mat_dorsalatt,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_dorsalatt$p.value

t_btw__mat_fpdm<- t.test(btw_hc_mat_fpdm,btw_mdd_mat_fpdm, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_fpdm$p.value
                   t_deg__mat_fpdm <- t.test(deg_hc_mat_fpdm,deg_mdd_mat_fpdm,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_fpdm$p.value

t_btw__mat_frparietal<- t.test(btw_hc_mat_frparietal,btw_mdd_mat_frparietal, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_frparietal$p.value
                   t_deg__mat_frparietal <- t.test(deg_hc_mat_frparietal,deg_mdd_mat_frparietal,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_frparietal$p.value

t_btw__mat_saldm<- t.test(btw_hc_mat_saldm,btw_mdd_mat_saldm, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_saldm$p.value
                   t_deg__mat_saldm <- t.test(deg_hc_mat_saldm,deg_mdd_mat_saldm,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_saldm$p.value

t_btw__mat_sali<- t.test(btw_hc_mat_sali,btw_mdd_mat_sali, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_sali$p.value
                   t_deg__mat_sali <- t.test(deg_hc_mat_sali,deg_mdd_mat_sali,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_sali$p.value

t_btw__mat_subc<- t.test(btw_hc_mat_subc,btw_mdd_mat_subc, alternative="two.sided",na.action=na.remove)
                   t_btw__mat_subc$p.value
                   t_deg__mat_subc <- t.test(deg_hc_mat_subc,deg_mdd_mat_subc,alternative="two.sided",na.action=na.remove)
                  t_deg__mat_subc$p.value


############# Creating a table for betweenness & centrality ############
tab_local <- matrix(c(t_deg$p.value,
                      t_btw$p.value,
                       t_deg__mat_cingdm$p.value,
                       t_btw__mat_cingdm$p.value,
                       t_deg__mat_cingop$p.value,
                       t_btw__mat_cingop$p.value,
                       t_deg__mat_dmode$p.value,
                       t_btw__mat_dmode$p.value,
                       t_deg__mat_dorsalatt$p.value,
                       t_btw__mat_dorsalatt$p.value,
                       t_deg__mat_fpdm$p.value,
                       t_btw__mat_fpdm$p.value,
                       t_deg__mat_frparietal$p.value,
                       t_btw__mat_frparietal$p.value,
                       t_deg__mat_saldm$p.value,
                       t_btw__mat_saldm$p.value,
                       t_deg__mat_sali$p.value,
                       t_btw__mat_sali$p.value,
                       t_deg__mat_subc$p.value,
                       t_btw__mat_subc$p.value
                       ), ncol=2, byrow=TRUE)
colnames(tab_local) <- c('degree','betweenness centrality')
rownames(tab_local) <- c('HC/MDD','HC cingdm/MDD cingdm','HC cingop/MDD cingop', 'HC DMN/MDD DMN', 'HC dorsalatt/MDD dorsalatt', 'HC fpdm/MDD fpdm','HC frparietal/MDD frparietal', 'HC saldm/MDD saldm', 'HC sali/MDD sali', 'HC subc/MDD subc')
write.table(tab_local, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/local.csv')


#Strength  #Sums edge weights for adjacent edges
str_hc_mat<- strength(i_hc_mat_p)
str_mdd_mat<- strength(i_mdd_mat_p)
ms_hc <- mean(str_hc_mat)
ms_mdd <- mean(str_mdd_mat)
t_str__mat <- t.test(str_hc_mat,str_mdd_mat, alternative="two.sided",na.action=na.remove)
                   t_str__mat$p.value

str_hc_mat_cingdm<- strength(i_hc_mat_cingdm_p)
                  str_mdd_mat_cingdm<- strength(i_mdd_mat_cingdm_p)
ms_hc_cingdm <- mean(str_hc_mat_cingdm)
ms_mdd_cingdm <- mean(str_mdd_mat_cingdm)
t_str__mat_cingdm <- t.test(str_hc_mat_cingdm,str_mdd_mat_cingdm, alternative="two.sided",na.action=na.remove)
                   t_str__mat_cingdm$p.value

                  str_hc_mat_cingop<- strength(i_hc_mat_cingop_p)
                  str_mdd_mat_cingop<- strength(i_mdd_mat_cingop_p)
ms_hc_cingop <-   mean(str_hc_mat_cingop)
ms_mdd_cingop <-   mean(str_mdd_mat_cingop)  
                  
t_str__mat_cingop <- t.test(str_hc_mat_cingop,str_mdd_mat_cingop, alternative="two.sided",na.action=na.remove)
                   t_str__mat_cingop$p.value
str_hc_mat_dmode<- strength(i_hc_mat_dmode_p)
                  str_mdd_mat_dmode<- strength(i_mdd_mat_dmode_p)
ms_hc_dmode <-   mean(str_hc_mat_dmode)
ms_mdd_dmode <-   mean(str_mdd_mat_dmode)
                  
 t_str__mat_dmode <- t.test(str_hc_mat_dmode,str_mdd_mat_dmode, alternative="two.sided",na.action=na.remove)
                   t_str__mat_dmode$p.value
str_hc_mat_dorsalatt<- strength(i_hc_mat_dorsalatt_p)
                  str_mdd_mat_dorsalatt<- strength(i_mdd_mat_dorsalatt_p)
ms_hc_dorsalatt <-   mean(str_hc_mat_dorsalatt)
ms_mdd_dorsalatt <-   mean(str_mdd_mat_dorsalatt)

 t_str__mat_dorsalatt <- t.test(str_hc_mat_dorsalatt,str_mdd_mat_dorsalatt, alternative="two.sided",na.action=na.remove)
                   t_str__mat_dorsalatt$p.value
str_hc_mat_fpdm<- strength(i_hc_mat_fpdm_p)
                  str_mdd_mat_fpdm<- strength(i_mdd_mat_fpdm_p)
ms_hc_fpdm      <-mean(str_hc_mat_fpdm)
ms_mdd_fpdm    <- mean(str_mdd_mat_fpdm)
                  
 t_str__mat_fpdm <- t.test(str_hc_mat_fpdm,str_mdd_mat_fpdm, alternative="two.sided",na.action=na.remove)
                   t_str__mat_fpdm$p.value
str_hc_mat_frparietal<- strength(i_hc_mat_frparietal_p)
                  str_mdd_mat_frparietal<- strength(i_mdd_mat_frparietal_p)
ms_hc_frparietal <-mean(str_hc_mat_frparietal)
ms_mdd_frparietal <-mean(str_mdd_mat_frparietal)
                  
 t_str__mat_frparietal <- t.test(str_hc_mat_frparietal,str_mdd_mat_frparietal, alternative="two.sided",na.action=na.remove)
                   t_str__mat_frparietal$p.value
str_hc_mat_saldm<- strength(i_hc_mat_saldm_p)
                  str_mdd_mat_saldm<- strength(i_mdd_mat_saldm_p)
ms_hc_saldm    <-mean(str_hc_mat_saldm)
ms_mdd_saldm <- mean(str_mdd_mat_saldm)
                  
 t_str__mat_saldm <- t.test(str_hc_mat_saldm,str_mdd_mat_saldm, alternative="two.sided",na.action=na.remove)
                   t_str__mat_saldm$p.value
str_hc_mat_sali<- strength(i_hc_mat_sali_p)
                  str_mdd_mat_sali<- strength(i_mdd_mat_sali_p)
ms_hc_sali <-      mean(str_hc_mat_sali)
ms_mdd_sali <-    mean(str_mdd_mat_sali)
                  
 t_str__mat_sali <- t.test(str_hc_mat_sali,str_mdd_mat_sali, alternative="two.sided",na.action=na.remove)
                   t_str__mat_sali$p.value
str_hc_mat_subc<- strength(i_hc_mat_subc_p)
                  str_mdd_mat_subc<- strength(i_mdd_mat_subc_p)
ms_hc_subc <-     mean(str_hc_mat_subc)
ms_mdd_subc <-    mean(str_mdd_mat_subc)
                  
 t_str__mat_subc <- t.test(str_hc_mat_subc,str_mdd_mat_subc, alternative="two.sided",na.action=na.remove)
                   t_str__mat_subc$p.value

                   
tab_strength <- matrix(c(ms_hc, t_str__mat$p.value,mb_hc,
  ms_mdd, t_str__mat$p.value,mb_mdd,
  ms_hc_cingdm, t_str__mat_cingdm$p.value,mb_hc_mat_cingdm,
  ms_mdd_cingdm, t_str__mat_cingdm$p.value,mb_mdd_mat_cingdm,
  ms_hc_cingop, t_str__mat_cingop$p.value,mb_hc_mat_cingop,
  ms_mdd_cingop, t_str__mat_cingop$p.value,mb_mdd_mat_cingop,
  ms_hc_dmode, t_str__mat_dmode$p.value,mb_hc_mat_dmode,
  ms_mdd_dmode, t_str__mat_dmode$p.value,mb_mdd_mat_dmode,
  ms_hc_dorsalatt, t_str__mat_dorsalatt$p.value,mb_hc_mat_dorsalatt,
  ms_mdd_dorsalatt, t_str__mat_dorsalatt$p.value,mb_mdd_mat_dorsalatt,
  ms_hc_fpdm, t_str__mat_fpdm$p.value,mb_hc_mat_fpdm,
  ms_mdd_fpdm, t_str__mat_fpdm$p.value,mb_mdd_mat_fpdm,
  ms_hc_frparietal, t_str__mat_frparietal$p.value,mb_hc_mat_frparietal,
  ms_mdd_frparietal, t_str__mat_frparietal$p.value,mb_mdd_mat_frparietal,
  ms_hc_saldm, t_str__mat_saldm$p.value,mb_hc_mat_saldm,
  ms_mdd_saldm, t_str__mat_saldm$p.value,mb_mdd_mat_saldm,
  ms_hc_sali, t_str__mat_sali$p.value,mb_hc_mat_sali,
  ms_mdd_sali, t_str__mat_sali$p.value,mb_mdd_mat_sali,
  ms_hc_subc, t_str__mat_subc$p.value,mb_hc_mat_subc,
  ms_mdd_subc, t_str__mat_subc$p.value,mb_mdd_mat_subc
                       ), ncol=3, byrow=TRUE)
colnames(tab_strength) <- c('mean strength','strength p-value','mean betweenness centrality')
rownames(tab_strength) <- c('HC','MDD','HC cingdm','MDD cingdm','HC cingop','MDD cingop', 'HC DMN','MDD DMN', 'HC dorsalatt','MDD dorsalatt', 'HC fpdm', 'MDD fpdm', 'HC frparietal','MDD frparietal', 'HC saldm','MDD saldm', 'HC sali','MDD sali', 'HC subc','MDD subc')
write.table(tab_strength, file='C:/Users/Katie/OneDrive - The Pennsylvania State University/b-geierlab Shared/Anhedonia/Cleaning&Analysis/SummaryTables/strength.csv')


#Strength Distribution  #Describes relative weight of edges for each node in network
sd_hc <- strength(i_hc_mat_p)
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,
       15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,
       73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,
       98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,
       116,117,118,119,120,121,122,123,124,125,126,127,128,
       129,130,131,132,133,134,135,136,137,138,139)

par(mar=c(5.1,4.7,4.0,2.1))
plot(x,sd_hc, ylim=c(4,16), main="Strength Distribution Across All Nodes (HC)", xlab="Node Number by Network", ylab="Strength of Adjacent Edges")
polygon(x=c(0,14,14,0),y=c(4,4,16.3,16.3), col="#FF9A98", density=12)
polygon(x=c(15,72,72,15),y=c(4,4,16.3,16.3), col="#FFF192", density=12)
polygon(x=c(73,97,97,73),y=c(4,4,16.3,16.3), col="#6ee387", density=12)
polygon(x=c(98,115,115,98),y=c(4,4,16.3,16.3), col="#7affff", density=12)
polygon(x=c(116,128,128,116),y=c(4,4,16.3,16.3), col="#87ceff", density=12)
polygon(x=c(129,139,139,129),y=c(4,4,16.3,16.3), col="#d2a0f9", density=12)
legend(x="topright",legend=c("cingulo-opercular","default mode","fronto-parietal","salience","subcortical","dorsal attention"),fill=c("#FF9A98","#FFF192","#6ee387","#7affff","#87ceff","#d2a0f9"))
library(Hmisc)
minor.tick(nx=5, ny=2)



sd_mdd <- strength(i_mdd_mat_p)
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,
       15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,
       73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,
       98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,
       116,117,118,119,120,121,122,123,124,125,126,127,128,
       129,130,131,132,133,134,135,136,137,138,139)
par(mar=c(5.1,4.7,4.0,2.1))
plot(x,sd_mdd,  ylim=c(4,16), main="Strength Distribution Across All Nodes (MDD)", xlab="Node Number", ylab="Strength of Adjacent Edges")
polygon(x=c(0,14,14,0),y=c(4,4,16.3,16.3), col="#FF9A98", density=12)
polygon(x=c(15,72,72,15),y=c(4,4,16.3,16.3), col="#FFF192", density=12)
polygon(x=c(73,97,97,73),y=c(4,4,16.3,16.3), col="#6ee387", density=12)
polygon(x=c(98,115,115,98),y=c(4,4,16.3,16.3), col="#7affff", density=12)
polygon(x=c(116,128,128,116),y=c(4,4,16.3,16.3), col="#87ceff", density=12)
polygon(x=c(129,139,139,129),y=c(4,4,16.3,16.3), col="#d2a0f9", density=12)
legend(x="topright",legend=c("cingulo-opercular","default mode","fronto-parietal","salience","subcortical","dorsal attention"),fill=c("#FF9A98","#FFF192","#6ee387","#7affff","#87ceff","#d2a0f9"))
library(Hmisc)
minor.tick(nx=5, ny=2)


t_sd <- t.test(sd_hc,sd_mdd,alternative="two.sided",na.action=na.remove)
t_sd$p.value


#####################################################################################
#Strength Distribution at r>0.2 threshold; Describes relative weight of edges for each node in network
threshold <- 0.2

# Apply thresholding
hc_mat_p_r2 <- ifelse(hc_mat_p > threshold, hc_mat_p, NA)
hc_mat_p_r2[is.na(hc_mat_p_r2)] <- 0
i_hc_mat_p_r2 <- graph.adjacency(hc_mat_p_r2, mode = 'undirected', weighted = TRUE)

  
sd_hc2 <- strength(i_hc_mat_p_r2)
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,
       15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,
       73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,
       98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,
       116,117,118,119,120,121,122,123,124,125,126,127,128,
       129,130,131,132,133,134,135,136,137,138,139)
par(mar=c(5.1,4.7,4.0,2.1))
plot(x,sd_hc2, ylim=c(4,16), main="Strength Distribution Across All Nodes (HC; r>0.2)", xlab="Node Number", ylab="Strength of Adjacent Edges")
polygon(x=c(0,14,14,0),y=c(3,3,16.3,16.3), col="#FF9A98", density=12)
polygon(x=c(15,72,72,15),y=c(3,3,16.3,16.3), col="#FFF192", density=12)
polygon(x=c(73,97,97,73),y=c(3,3,16.3,16.3), col="#6ee387", density=12)
polygon(x=c(98,115,115,98),y=c(3,3,16.3,16.3), col="#7affff", density=12)
polygon(x=c(116,128,128,116),y=c(3,3,16.3,16.3), col="#87ceff", density=12)
polygon(x=c(129,139,139,129),y=c(3,3,16.3,16.3), col="#d2a0f9", density=12)
legend(x="topright",legend=c("cingulo-opercular","default mode","fronto-parietal","salience","subcortical","dorsal attention"),fill=c("#FF9A98","#FFF192","#6ee387","#7affff","#87ceff","#d2a0f9"))
library(Hmisc)
minor.tick(nx=5, ny=2)


###############################################
threshold <- 0.2

# Apply thresholding
mdd_mat_p_r2 <- ifelse(mdd_mat_p > threshold, mdd_mat_p, NA)
mdd_mat_p_r2[is.na(mdd_mat_p_r2)] <- 0
i_mdd_mat_p_r2 <- graph.adjacency(mdd_mat_p_r2, mode = 'undirected', weighted = TRUE)


sd_mdd2 <- strength(i_mdd_mat_p_r2)
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,
       15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,
       73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,
       98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,
       116,117,118,119,120,121,122,123,124,125,126,127,128,
       129,130,131,132,133,134,135,136,137,138,139)
par(mar=c(5.1,4.7,4.0,2.1))
plot(x,sd_mdd2,  ylim=c(4,16), main="Strength Distribution Across All Nodes (MDD; r>0.2)", xlab="Node Number", ylab="Strength of Adjacent Edges")
polygon(x=c(0,14,14,0),y=c(3,3,16.3,16.3), col="#FF9A98", density=12)
polygon(x=c(15,72,72,15),y=c(3,3,16.3,16.3), col="#FFF192", density=12)
polygon(x=c(73,97,97,73),y=c(3,3,16.3,16.3), col="#6ee387", density=12)
polygon(x=c(98,115,115,98),y=c(3,3,16.3,16.3), col="#7affff", density=12)
polygon(x=c(116,128,128,116),y=c(3,3,16.3,16.3), col="#87ceff", density=12)
polygon(x=c(129,139,139,129),y=c(3,3,16.3,16.3), col="#d2a0f9", density=12)
legend(x="topright",legend=c("cingulo-opercular","default mode","fronto-parietal","salience","subcortical","dorsal attention"),fill=c("#FF9A98","#FFF192","#6ee387","#7affff","#87ceff","#d2a0f9"))
library(Hmisc)
minor.tick(nx=5, ny=2)



#Strength Distribution at r>0.3 threshold; Describes relative weight of edges for each node in network
threshold3 <- 0.3

# Apply thresholding
hc_mat_p_r3 <- ifelse(hc_mat_p > threshold3, hc_mat_p, NA)
hc_mat_p_r3[is.na(hc_mat_p_r3)] <- 0
i_hc_mat_p_r3 <- graph.adjacency(hc_mat_p_r3, mode = 'undirected', weighted = TRUE)


sd_hc <- strength(i_hc_mat_p_r3)
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,
       15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,
       73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,
       98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,
       116,117,118,119,120,121,122,123,124,125,126,127,128,
       129,130,131,132,133,134,135,136,137,138,139)
par(mar=c(5.1,4.7,4.0,2.1))
plot(x,sd_hc, ylim=c(4,16), main="Strength Distribution Across All Nodes (HC; r>0.3)", xlab="Node Number", ylab="Strength of Adjacent Edges")
polygon(x=c(0,14,14,0),y=c(3,3,16.3,16.3), col="#FF9A98", density=12)
polygon(x=c(15,72,72,15),y=c(3,3,16.3,16.3), col="#FFF192", density=12)
polygon(x=c(73,97,97,73),y=c(3,3,16.3,16.3), col="#6ee387", density=12)
polygon(x=c(98,115,115,98),y=c(3,3,16.3,16.3), col="#7affff", density=12)
polygon(x=c(116,128,128,116),y=c(3,3,16.3,16.3), col="#87ceff", density=12)
polygon(x=c(129,139,139,129),y=c(3,3,16.3,16.3), col="#d2a0f9", density=12)
legend(x="topright",legend=c("cingulo-opercular","default mode","fronto-parietal","salience","subcortical","dorsal attention"),fill=c("#FF9A98","#FFF192","#6ee387","#7affff","#87ceff","#d2a0f9"))
library(Hmisc)
minor.tick(nx=5, ny=2)


# Apply thresholding
mdd_mat_p_r3 <- ifelse(mdd_mat_p > threshold3, mdd_mat_p, NA)
mdd_mat_p_r3[is.na(mdd_mat_p_r3)] <- 0
i_mdd_mat_p_r3 <- graph.adjacency(mdd_mat_p_r3, mode = 'undirected', weighted = TRUE)


sd_mdd3 <- strength(i_mdd_mat_p_r3)
x <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,
       15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,
       73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,
       98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,
       116,117,118,119,120,121,122,123,124,125,126,127,128,
       129,130,131,132,133,134,135,136,137,138,139)
par(mar=c(5.1,4.7,4.0,2.1))
plot(x,sd_mdd3,  ylim=c(4,16), main="Strength Distribution Across All Nodes (MDD; r>0.3)", xlab="Node Number", ylab="Strength of Adjacent Edges")
polygon(x=c(0,14,14,0),y=c(3,3,16.3,16.3), col="#FF9A98", density=12)
polygon(x=c(15,72,72,15),y=c(3,3,16.3,16.3), col="#FFF192", density=12)
polygon(x=c(73,97,97,73),y=c(3,3,16.3,16.3), col="#6ee387", density=12)
polygon(x=c(98,115,115,98),y=c(3,3,16.3,16.3), col="#7affff", density=12)
polygon(x=c(116,128,128,116),y=c(3,3,16.3,16.3), col="#87ceff", density=12)
polygon(x=c(129,139,139,129),y=c(3,3,16.3,16.3), col="#d2a0f9", density=12)
legend(x="topright",legend=c("cingulo-opercular","default mode","fronto-parietal","salience","subcortical","dorsal attention"),fill=c("#FF9A98","#FFF192","#6ee387","#7affff","#87ceff","#d2a0f9"))
library(Hmisc)
minor.tick(nx=5, ny=2)
```


Centrality
```{r}
#Betweenness centrality of some vertices:
#igraph_error_t 
igraph_betweenness(const igraph_t *graph, igraph_vector_t *res,
                       const igraph_vs_t vids, igraph_bool_t directed,
                       const igraph_vector_t* weights);
btw_hc <- betweenness(i_hc_mat_p,v = V(i_hc_mat_p))
btw_mdd <- betweenness(i_mdd_mat_p,v = V(i_mdd_mat_p))

#Betweenness centrality of the edges.
#igraph_error_t 
igraph_edge_betweenness(const igraph_t *graph, igraph_vector_t *result,
                            igraph_bool_t directed,
                            const igraph_vector_t *weights);


```

In the future, it may be useful to create a function to do all of this with less code. Using dplyr, as I did above, can run into issues when creating functions. However, website below seems to have a general solution that should work across dplyr commands.

https://medium.com/optima-blog/writing-your-own-dplyr-functions-a1568720db0d